# Results

```{r setup-04}
# Load packages and data
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(knitr)
library(kableExtra)
library(magrittr)
library(here)
source(here("src/funs.R"))
ivst <- readRDS(here("data/iv_summary_train.rds"))
ivsts1 <- readRDS(here("data/iv_summary_train_step1.rds"))
ivsts2 <- readRDS(here("data/iv_summary_train_step2.rds"))
ivs1 <- readRDS(here("data/iv_summary_cs1_all.rds"))
ivs2 <- readRDS(here("data/iv_summary_cs2_all.rds"))
```

```{r ivs-combine}
ivst <- ivst %>% mutate(sampling = fct_inorder(sampling))
ivsts1 <- ivsts1 %>% mutate(sampling = fct_inorder(sampling))
ivsts2 <- ivsts2 %>% mutate(sampling = fct_inorder(sampling))
ivs1 <- ivs1 %>% mutate(sampling = fct_inorder(sampling))
ivs2 <- ivs2 %>% mutate(sampling = fct_inorder(sampling))
ivs <- bind_rows(ivst, ivs1, ivs2) %>%
  mutate(dataset = factor(
    dataset,
    levels = c("train", "cs1_all", "cs2_all"),
    labels = c("Training", "CS1", "CS2")
  ),
  sampling = fct_inorder(sampling))
```

We show internal validation summaries for the combined classifier training set, as well as the CS1 and CS2 sets with duplicates included. The F1-scores, kappa, and G-mean are the measures of interest. Algorithms are sorted by descending value based on the overallaccuracy of the training set. The point ranges show the median, 5th and 95th percentiles, coloured by subsampling methods.

## Training Set

### Accuracy

```{r train-accuracy, fig.cap='Training Set Accuracy'}
ivst_accuracy <- ivst %>% 
  filter(measure == "accuracy") %>% 
  mutate(algorithm = fct_reorder2(algorithm, sampling, percentile_50))

alg_levels <- levels(ivst_accuracy[["algorithm"]])

p <- plot_measure(ivst_accuracy) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-accuracy-table}
ivst_accuracy_table <- ivst_accuracy %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_accuracy_table,
      caption = "Training Set Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-accuracy-class, fig.cap='Training Set Class-Specific Accuracy', fig.width=8}
ivst_accuracy_class <- ivst %>%
  filter(grepl("accuracy\\.", measure)) %>%
  mutate(
    measure = gsub("accuracy\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivst_accuracy_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Class-Specific Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-accuracy-class-table}
ivst_accuracy_class_table <- ivst_accuracy_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_accuracy_class_table,
      caption = "Training Set Class-Specific Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### F1-Score

```{r train-f1, fig.cap='Training Set F1-Score'}
ivst_f1 <- ivst %>%
  filter(measure == "macro_f1") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivst_f1) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Macro-Averaged F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-f1-table}
ivst_f1_table <- ivst_f1 %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_f1_table,
      caption = "Training Set Macro-Averaged F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-f1-class, fig.cap='Training Set Class-Specific F1-Score', fig.width=8}
ivst_f1_class <- ivst %>%
  filter(grepl("f1\\.", measure)) %>%
  mutate(
    measure = gsub("f1\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivst_f1_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Class-Specific F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-f1-class-table}
ivst_f1_class_table <- ivst_f1_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_f1_class_table,
      caption = "Training Set Class-Specific F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### Kappa

```{r train-kappa, fig.cap='Training Set Kappa'}
ivst_kappa <- ivst %>%
  filter(measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivst_kappa) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-kappa-table}
ivst_kappa_table <- ivst_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_kappa_table,
      caption = "Training Set Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-kappa-class, fig.cap='Training Set Class-Specific Kappa', fig.width=8}
ivst_kappa_class <- ivst %>%
  filter(grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivst_kappa_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Class-Specific Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-kappa-class-table}
ivst_kappa_class_table <- ivst_kappa_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_kappa_class_table,
      caption = "Training Set Class-Specific Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### G-mean

```{r train-gmean, fig.cap='Training Set G-mean'}
ivst_gmean <- ivst %>%
  filter(measure == "gmean") %>%
  mutate(
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivst_gmean) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-gmean-table}
ivst_gmean_table <- ivst_gmean %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_gmean_table,
      caption = "Training Set G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-gmean-class, fig.cap='Training Set Class-Specific G-mean', fig.width=8}
ivst_gmean_class <- ivst %>%
  filter(grepl("gmean\\.", measure)) %>%
  mutate(
    measure = gsub("gmean\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivst_gmean_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set Class Specific G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-gmean-class-table}
ivst_gmean_class_table <- ivst_gmean_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivst_gmean_class_table,
      caption = "Training Set Class-Specific G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

## Two-Step Training Set

### Accuracy

```{r train-step1-accuracy, fig.cap='Training Set Step 1 Accuracy'}
ivsts1_accuracy <- ivsts1 %>% 
  filter(measure == "accuracy") %>% 
  mutate(algorithm = fct_reorder2(algorithm, sampling, percentile_50))

alg_levels <- levels(ivsts1_accuracy[["algorithm"]])

p <- plot_measure(ivsts1_accuracy) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Step 1 Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-accuracy, fig.cap='Training Set Step 2 Accuracy'}
ivsts2_accuracy <- ivsts2 %>% 
  filter(measure == "accuracy") %>% 
  mutate(algorithm = fct_reorder2(algorithm, sampling, percentile_50))

alg_levels <- levels(ivsts2_accuracy[["algorithm"]])

p <- plot_measure(ivsts2_accuracy) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Step 2 Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-accuracy-table}
ivsts1_accuracy_table <- ivsts1_accuracy %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_accuracy_table,
      caption = "Training Set Step 1 Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step2-accuracy-table}
ivsts2_accuracy_table <- ivsts2_accuracy %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_accuracy_table,
      caption = "Training Set Step 2 Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step1-accuracy-class, fig.cap='Training Set Step 1 Class-Specific Accuracy', fig.width=8}
ivsts1_accuracy_class <- ivsts1 %>%
  filter(grepl("accuracy\\.", measure)) %>%
  mutate(
    measure = gsub("accuracy\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts1_accuracy_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Step 1 Class-Specific Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-accuracy-class, fig.cap='Training Set Step 2 Class-Specific Accuracy', fig.width=8}
ivsts2_accuracy_class <- ivsts2 %>%
  filter(grepl("accuracy\\.", measure)) %>%
  mutate(
    measure = gsub("accuracy\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts2_accuracy_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "Training Set Step 2 Class-Specific Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-accuracy-class-table}
ivsts1_accuracy_class_table <- ivsts1_accuracy_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_accuracy_class_table,
      caption = "Training Set Step 1 Class-Specific Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-step2-accuracy-class-table}
ivsts2_accuracy_class_table <- ivsts2_accuracy_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_accuracy_class_table,
      caption = "Training Set Step 2 Class-Specific Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### F1-Score

```{r train-step1-f1, fig.cap='Training Set Step 1 F1-Score'}
ivsts1_f1 <- ivsts1 %>%
  filter(measure == "macro_f1") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivsts1_f1) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Step 1 Macro-Averaged F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-f1, fig.cap='Training Set Step 2 F1-Score'}
ivsts2_f1 <- ivsts2 %>%
  filter(measure == "macro_f1") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivsts2_f1) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Step 2 Macro-Averaged F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-f1-table}
ivsts1_f1_table <- ivsts1_f1 %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_f1_table,
      caption = "Training Set Step 1 Macro-Averaged F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-step2-f1-table}
ivsts2_f1_table <- ivsts2_f1 %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_f1_table,
      caption = "Training Set Step 2 Macro-Averaged F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-step1-f1-class, fig.cap='Training Set Step 1 Class-Specific F1-Score', fig.width=8}
ivsts1_f1_class <- ivsts1 %>%
  filter(grepl("f1\\.", measure)) %>%
  mutate(
    measure = gsub("f1\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts1_f1_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Step 1 Class-Specific F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-f1-class, fig.cap='Training Set Step 2 Class-Specific F1-Score', fig.width=8}
ivsts2_f1_class <- ivsts2 %>%
  filter(grepl("f1\\.", measure)) %>%
  mutate(
    measure = gsub("f1\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts2_f1_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "Training Set Step 2 Class-Specific F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-f1-class-table}
ivsts1_f1_class_table <- ivsts1_f1_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_f1_class_table,
      caption = "Training Set Step 1 Class-Specific F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-step2-f1-class-table}
ivsts2_f1_class_table <- ivsts2_f1_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_f1_class_table,
      caption = "Training Set Step 2 Class-Specific F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### Kappa

```{r train-step1-kappa, fig.cap='Training Set Step 1 Kappa'}
ivsts1_kappa <- ivsts1 %>%
  filter(measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivsts1_kappa) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Step 1 Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-kappa, fig.cap='Training Set Step 2 Kappa'}
ivsts2_kappa <- ivsts2 %>%
  filter(measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivsts2_kappa) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Step 2 Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-kappa-table}
ivsts1_kappa_table <- ivsts1_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_kappa_table,
      caption = "Training Set Step 1 Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step2-kappa-table}
ivsts2_kappa_table <- ivsts2_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_kappa_table,
      caption = "Training Set Step 2 Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step1-kappa-class, fig.cap='Training Set Step 1 Class-Specific Kappa', fig.width=8}
ivsts1_kappa_class <- ivsts1 %>%
  filter(grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts1_kappa_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Step 1 Class-Specific Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-kappa-class, fig.cap='Training Set Step 2 Class-Specific Kappa', fig.width=8}
ivsts2_kappa_class <- ivsts2 %>%
  filter(grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts2_kappa_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "Training Set Step 2 Class-Specific Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-kappa-class-table}
ivsts1_kappa_class_table <- ivsts1_kappa_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_kappa_class_table,
      caption = "Training Set Step 1 Class-Specific Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r train-step2-kappa-class-table}
ivsts2_kappa_class_table <- ivsts2_kappa_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_kappa_class_table,
      caption = "Training Set Step 2 Class-Specific Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### G-mean

```{r train-step1-gmean, fig.cap='Training Set Step 1 G-mean'}
ivsts1_gmean <- ivsts1 %>%
  filter(measure == "gmean") %>%
  mutate(
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts1_gmean) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set Step 1 G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-gmean, fig.cap='Training Set Step 2 G-mean'}
ivsts2_gmean <- ivsts2 %>%
  filter(measure == "gmean") %>%
  mutate(
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts2_gmean) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set Step 2 G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-gmean-table}
ivsts1_gmean_table <- ivsts1_gmean %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_gmean_table,
      caption = "Training Set Step 1 G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step2-gmean-table}
ivsts2_gmean_table <- ivsts2_gmean %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_gmean_table,
      caption = "Training Set Step 2 G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r train-step1-gmean-class, fig.cap='Training Set Step 1 Class-Specific G-mean', fig.width=8}
ivsts1_gmean_class <- ivsts1 %>%
  filter(grepl("gmean\\.", measure)) %>%
  mutate(
    measure = gsub("gmean\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts1_gmean_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set Step 1 Class Specific G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step2-gmean-class, fig.cap='Training Set Step 2 Class-Specific G-mean', fig.width=8}
ivsts2_gmean_class <- ivsts2 %>%
  filter(grepl("gmean\\.", measure)) %>%
  mutate(
    measure = gsub("gmean\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivsts2_gmean_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "Training Set Step 2 Class Specific G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r train-step1-gmean-class-table}
ivsts1_gmean_class_table <- ivsts1_gmean_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts1_gmean_class_table,
      caption = "Training Set Step 1 Class-Specific G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```







```{r train-step2-gmean-class-table}
ivsts2_gmean_class_table <- ivsts2_gmean_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivsts2_gmean_class_table,
      caption = "Training Set Step 2 Class-Specific G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

## CS1 Set

### Accuracy

```{r cs1-accuracy, fig.cap='CS1 Set Accuracy'}
ivs1_accuracy <- ivs1 %>%
  filter(measure == "accuracy") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs1_accuracy) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "CS1 Set Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-accuracy-table}
ivs1_accuracy_table <- ivs1_accuracy %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_accuracy_table,
      caption = "CS1 Set Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs1-accuracy-class, fig.cap='CS1 Set Class-Specific Accuracy', fig.width=8}
ivs1_accuracy_class <- ivs1 %>%
  filter(grepl("accuracy\\.", measure)) %>%
  mutate(
    measure = gsub("accuracy\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs1_accuracy_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "CS1 Set Class-Specific Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-accuracy-class-table}
ivs1_accuracy_class_table <- ivs1_accuracy_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_accuracy_class_table,
      caption = "CS1 Set Class-Specific Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### F1-Score

```{r cs1-f1, fig.cap='CS1 Set F1-Score'}
ivs1_f1 <- ivs1 %>%
  filter(measure == "macro_f1") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs1_f1) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "CS1 Set Macro-Averaged F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-f1-table}
ivs1_f1_table <- ivs1_f1 %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_f1_table,
      caption = "CS1 Set Macro-Averaged F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r cs1-f1-class, fig.cap='CS1 Set Class-Specific F1-Score', fig.width=8}
ivs1_f1_class <- ivs1 %>%
  filter(grepl("f1\\.", measure)) %>%
  mutate(
    measure = gsub("f1\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs1_f1_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "CS1 Set Class-Specific F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-f1-class-table}
ivs1_f1_class_table <- ivs1_f1_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_f1_class_table,
      caption = "CS1 Set Class-Specific F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### Kappa

```{r cs1-kappa, fig.cap='CS1 Set Kappa'}
ivs1_kappa <- ivs1 %>%
  filter(measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs1_kappa) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "CS1 Set Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-kappa-table}
ivs1_kappa_table <- ivs1_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_kappa_table,
      caption = "CS1 Set Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs1-kappa-class, fig.cap='CS1 Set Class-Specific Kappa', fig.width=8}
ivs1_kappa_class <- ivs1 %>%
  filter(grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs1_kappa_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "CS1 Set Class-Specific Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-kappa-class-table}
ivs1_kappa_class_table <- ivs1_kappa_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_kappa_class_table,
      caption = "CS1 Set Class-Specific Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### G-mean

```{r cs1-gmean, fig.cap='CS1 Set G-mean'}
ivs1_gmean <- ivs1 %>%
  filter(measure == "gmean") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs1_gmean) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "CS1 Set G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-gmean-table}
ivs1_gmean_table <- ivs1_gmean %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_gmean_table,
      caption = "CS1 Set G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs1-gmean-class, fig.cap='CS1 Set Class-Specific G-mean', fig.width=8}
ivs1_gmean_class <- ivs1 %>%
  filter(grepl("gmean\\.", measure)) %>%
  mutate(
    measure = gsub("gmean\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs1_gmean_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "CS1 Set Class Specific G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs1-gmean-class-table}
ivs1_gmean_class_table <- ivs1_gmean_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs1_gmean_class_table,
      caption = "CS1 Set Class-Specific G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

## CS2 Set

### Accuracy

```{r cs2-accuracy, fig.cap='CS2 Set Accuracy'}
ivs2_accuracy <- ivs2 %>%
  filter(measure == "accuracy") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs2_accuracy) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "CS2 Set Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-accuracy-table}
ivs2_accuracy_table <- ivs2_accuracy %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_accuracy_table,
      caption = "CS2 Set Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs2-accuracy-class, fig.cap='CS2 Set Class-Specific Accuracy', fig.width=8}
ivs2_accuracy_class <- ivs2 %>%
  filter(grepl("accuracy\\.", measure)) %>%
  mutate(
    measure = gsub("accuracy\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs2_accuracy_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Accuracy",
    color = "Subsampling",
    title = "CS2 Set Class-Specific Accuracy by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-accuracy-class-table}
ivs2_accuracy_class_table <- ivs2_accuracy_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_accuracy_class_table,
      caption = "CS2 Set Class-Specific Accuracy by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### F1-Score

```{r cs2-f1, fig.cap='CS2 Set F1-Score'}
ivs2_f1 <- ivs2 %>%
  filter(measure == "macro_f1") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs2_f1) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "CS2 Set Macro-Averaged F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-f1-table}
ivs2_f1_table <- ivs2_f1 %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_f1_table,
      caption = "CS2 Set Macro-Averaged F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

```{r cs2-f1-class, fig.cap='CS2 Set Class-Specific F1-Score', fig.width=8}
ivs2_f1_class <- ivs2 %>%
  filter(grepl("f1\\.", measure)) %>%
  mutate(
    measure = gsub("f1\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs2_f1_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "F1-Score",
    color = "Subsampling",
    title = "CS2 Set Class-Specific F1-Score by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-f1-class-table}
ivs2_f1_class_table <- ivs2_f1_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_f1_class_table,
      caption = "CS2 Set Class-Specific F1-Score by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### Kappa

```{r cs2-kappa, fig.cap='CS2 Set Kappa'}
ivs2_kappa <- ivs2 %>%
  filter(measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs2_kappa) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "CS2 Set Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-kappa-table}
ivs2_kappa_table <- ivs2_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_kappa_table,
      caption = "CS2 Set Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs2-kappa-class, fig.cap='CS2 Set Class-Specific Kappa', fig.width=8}
ivs2_kappa_class <- ivs2 %>%
  filter(grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs2_kappa_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "Kappa",
    color = "Subsampling",
    title = "CS2 Set Class-Specific Kappa by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-kappa-class-table}
ivs2_kappa_class_table <- ivs2_kappa_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_kappa_class_table,
      caption = "CS2 Set Class-Specific Kappa by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

### G-mean

```{r cs2-gmean, fig.cap='CS2 Set G-mean'}
ivs2_gmean <- ivs2 %>%
  filter(measure == "gmean") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <- plot_measure(ivs2_gmean) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "CS2 Set G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-gmean-table}
ivs2_gmean_table <- ivs2_gmean %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = sampling,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_gmean_table,
      caption = "CS2 Set G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()  
```

```{r cs2-gmean-class, fig.cap='CS2 Set Class-Specific G-mean', fig.width=8}
ivs2_gmean_class <- ivs2 %>%
  filter(grepl("gmean\\.", measure)) %>%
  mutate(
    measure = gsub("gmean\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <- plot_measure(ivs2_gmean_class) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    y = "G-mean",
    color = "Subsampling",
    title = "CS2 Set Class Specific G-mean by Algorithm and Subsampling Method"
  )
print(p)
```

```{r cs2-gmean-class-table}
ivs2_gmean_class_table <- ivs2_gmean_class %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  rename(histotype = measure) %>% 
  pivot_wider(id_cols = sampling:histotype,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs2_gmean_class_table,
      caption = "CS2 Set Class-Specific G-mean by Algorithm and Subsampling Method",
      escape = FALSE) %>%
  kable_styling()
```

## SMOTE Kappa Summary

```{r smote-kappa, fig.cap='SMOTE Kappa by Algorithm and Dataset'}
ivs_smote_kappa <- ivs %>%
  filter(sampling == "smote", measure == "kappa") %>%
  mutate(algorithm = factor(algorithm, levels = alg_levels))

p <-
  ggplot(ivs_smote_kappa, aes(x = algorithm, y = percentile_50, color = dataset)) +
  geom_pointrange(aes(ymin = percentile_5, ymax = percentile_95),
                  position = position_dodge(width = 0.4)) +
  
  theme_bw() +
  theme(plot.title = element_text(face = "bold")) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "Algorithm",
    y = "Kappa",
    color = "Dataset",
    title = "SMOTE Kappa by Algorithm and Dataset"
  )
print(p)
```

```{r smote-kappa-table}
ivs_smote_kappa_table <- ivs_smote_kappa %>%
  arrange(algorithm) %>%
  mutate(across(where(is.numeric), round, digits = 3)) %>%
  mutate(percentile_50 = ifelse(
    percentile_50 == max(percentile_50),
    cell_spec(percentile_50, bold = TRUE),
    percentile_50
  )) %>%
  pivot_wider(id_cols = dataset,
              names_from = "algorithm",
              values_from = "percentile_50") %>% 
  rename_with(~ gsub("_", "\\\\_", .), matches("_"))

kable(ivs_smote_kappa_table,
      caption = "SMOTE Kappa by Algorithm and Dataset",
      escape = FALSE) %>%
  kable_styling()  
```

```{r smote-kappa-class, fig.cap='SMOTE Class-Specific Kappa by Algorithm and Dataset', fig.width=8}
ivs_smote_kappa_class <- ivs %>%
  filter(sampling == "smote", grepl("kappa\\.", measure)) %>%
  mutate(
    measure = gsub("kappa\\.", "", measure),
    algorithm = factor(algorithm, levels = alg_levels)
  )

p <-
  ggplot(ivs_smote_kappa_class, aes(x = algorithm, y = percentile_50, color = dataset)) +
  geom_pointrange(aes(ymin = percentile_5, ymax = percentile_95),
                  position = position_dodge(width = 0.4)) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(plot.title = element_text(face = "bold")) +
  facet_wrap(vars(measure), ncol = 2) +
  labs(
    x = "Algorithm",
    y = "Kappa",
    color = "Dataset",
    title = "SMOTE Class-Specific Kappa by Algorithm and Dataset"
  )
print(p)
```
