# Results

```{r}
#| label: setup-results

# Load packages and data
library(dplyr)
library(purrr)
library(tibble)
library(tidyr)
library(ggplot2)
library(forcats)
library(cli)
library(knitr)
library(kableExtra)
library(RankAggreg)
library(DT)
library(plotly)
library(patchwork)
library(tidymodels)
library(themis)
library(RColorBrewer)
library(ggh4x)
library(ggtext)
library(ggrepel)
library(ggpubr)
library(randomForest)
library(here)
library(DESeq2)
library(tabulapdf)
library(janitor)
library(flextable)
library(probably)
library(vip)
library(conflicted)

# Choose preferences among conflicting functions
conflicts_prefer(
  ggplot2::margin(),
  purrr::set_names(),
  dplyr::filter(),
  nanostringr::HKnorm(),
  plotly::rename(),
  base::setdiff(),
  dplyr::count(),
  purrr::reduce(),
  base::intersect(),
  base::union(),
  flextable::width(),
  plotly::layout(),
  ggplot2::last_plot(),
  yardstick::accuracy()
)

# Run cohort processing
source(here("validation/cs_process_cohorts.R"))
source(here("src/funs.R"))

## Inputs
# Training data
train_data <- readRDS(here("data", "train_data.rds"))
train_class <- readRDS(here("data", "train_class.rds"))

# Confirmation data
conf_data <- readRDS(here("data", "conf_data.rds"))
conf_class <- readRDS(here("data", "conf_class.rds"))

# Validation data
val_data <- readRDS(here("data", "val_data.rds"))
val_class <- readRDS(here("data", "val_class.rds"))

# Sequential data
seq_data <- readRDS(here("data", "seq_data.rds"))
seq_class <- readRDS(here("data", "seq_class.rds"))

# Two-step data
two_step_data <- readRDS(here("data", "two_step_data.rds"))
two_step_class <- readRDS(here("data", "two_step_class.rds"))

# Confirmation data with all PrOTYPE and SPOT genes
conf_full_data <- readRDS(here("data", "conf_full_data.rds"))
conf_full_class <- readRDS(here("data", "conf_full_class.rds"))

# Validation data with all PrOTYPE and SPOT genes
val_full_data <- readRDS(here("data", "val_full_data.rds"))
val_full_class <- readRDS(here("data", "val_full_class.rds"))

## Outputs
# Training Set Metrics
all_metrics_train <- readRDS(here("data/all_metrics_train.rds"))
per_class_metrics_seq <-
  readRDS(here("data/per_class_metrics_seq.rds"))
per_class_metrics_two_step <-
  readRDS(here("data/per_class_metrics_two_step.rds"))

# Confirmation Set Metrics
all_metrics_conf <- readRDS(here("data/all_metrics_conf.rds"))
per_class_metrics_conf_seq <-
  readRDS(here("data/per_class_metrics_conf_seq.rds"))
per_class_metrics_conf_two_step <-
  readRDS(here("data/per_class_metrics_conf_two_step.rds"))

# Alternate Confirmation Set Metrics
all_metrics_conf_opt <- readRDS(here("data/all_metrics_conf_opt.rds"))
all_metrics_conf_base <- readRDS(here("data/all_metrics_conf_base.rds"))
all_metrics_conf_full <- readRDS(here("data/all_metrics_conf_full.rds"))

# Training Set Models
wflow_up_rf_model <- readRDS(here("data/wflow_up_rf_model_train.rds"))
wflow_smote_svm_model <- readRDS(here("data/wflow_smote_svm_model_train.rds"))
wflow_hybrid_xgb_model <- readRDS(here("data/wflow_hybrid_xgb_model_train.rds"))
all_models_seq <- readRDS(here("data/all_models_seq.rds"))
all_models_two_step <- readRDS(here("data/all_models_two_step.rds"))

# Overall Variable Importance
all_vi_train <- readRDS(here("data/all_vi_train.rds"))
all_vi_seq <- readRDS(here("data/all_vi_seq.rds"))
all_vi_two_step <- readRDS(here("data/all_vi_two_step.rds"))

# Gene Optimization
gene_opt_de_all_metrics_conf <- 
  readRDS(here("data/gene_opt_de_all_metrics_conf.rds"))
gene_opt_all_metrics_conf <- 
  readRDS(here("data/gene_opt_all_metrics_conf.rds"))
gene_opt_all_metrics_conf_seq <-
  readRDS(here("data/gene_opt_all_metrics_conf_seq.rds"))
gene_opt_all_metrics_conf_two_step <-
  readRDS(here("data/gene_opt_all_metrics_conf_two_step.rds"))

# PrOTYPE and SPOT genes
overlap_PrOTYPE <- intersect(names(train_data), genes_PrOTYPE)
overlap_SPOT <- intersect(names(train_data), genes_SPOT)
overlap_all <- union(overlap_PrOTYPE, overlap_SPOT)

# PrOTYPE final model
final_model <- readRDS(here("data/final_model.rds"))

# DOVE consolidated IHC scores
final_scores <- read_excel(here("data-raw/CT14-05_Scores-Deconvoluted-Summarized_MA27SEPT2016/outputs/final_scores.xlsx"))

# Histotypes colour palette
class_palette <- brewer.pal(n = 5, name = "Dark2")
```

We summarize cross-validated training performance of class metrics in the training set. The accuracy, F1-score, and kappa, are the metrics of interest. Workflows are ordered by their mean estimates across the outer folds of the nested CV for each metric.

## Training Set

```{r}
#| label: train-metrics

all_metrics_train <- all_metrics_train |> 
  separate(wflow, c("Subsampling", "Algorithms"), remove = FALSE) |> 
  mutate(
    Subsampling = factor(Subsampling, levels = c("none", "down", "up", "smote", "hybrid")),
    Algorithms = factor(Algorithms, levels = c("rf", "svm", "xgb", "mr")),
    class_group = factor(
      class_group,
      levels = c("Overall", "HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC")
    )
  ) |> 
  mutate(
    lower = ifelse(all(is.na(.estimate)), NA, min(.estimate, na.rm = TRUE)),
    upper = ifelse(all(is.na(.estimate)), NA, max(.estimate, na.rm = TRUE)),
    .by = c(wflow, class_group, .metric)
  ) |>
  mutate(
    undefined = case_when(any(is.nan(mean_estimate)) ~ "all",
                          any(is.na(.estimate)) ~ "some",
                          .default = "none"),
    .by = c(wflow, .metric)
  )
```

::: {#training-set-results .panel-tabset .nav-pills}
### Accuracy

```{r}
#| label: tbl-train-accuracy
#| tbl-cap: 'Training Set Mean Accuracy'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "accuracy") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-accuracy
#| fig-cap: 'Training Set Mean Accuracy'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "accuracy"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "Accuracy",
       title = "Training Set Mean Accuracy")
print(p)
```

### Sensitivity

```{r}
#| label: tbl-train-sens
#| tbl-cap: 'Training Set Mean Sensitivity'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "sensitivity") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-sens
#| fig-cap: 'Training Set Mean Sensitivity'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "sensitivity"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "Sensitivity",
       title = "Training Set Mean Sensitivity")
print(p)
```

### Specificity

```{r}
#| label: tbl-train-spec
#| tbl-cap: 'Training Set Mean Specificity'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "specificity") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-spec
#| fig-cap: 'Training Set Mean Specificity'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "specificity"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "Specificity",
       title = "Training Set Mean Specificity")
print(p)
```

### F1-Score

```{r}
#| label: tbl-train-f1
#| tbl-cap: 'Training Set Mean F1-Score'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "f_meas") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-f1
#| fig-cap: 'Training Set Mean F1-Score'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "f_meas"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "F1-Score",
       title = "Training Set Mean F1-Score")
print(p)
```

### Balanced Accuracy

```{r}
#| label: tbl-train-bal-accuracy
#| tbl-cap: 'Training Set Mean Balanced Accuracy'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "bal_accuracy") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-bal-accuracy
#| fig-cap: 'Training Set Mean Balanced Accuracy'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "bal_accuracy"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "Balanced Accuracy",
       title = "Training Set Mean Balanced Accuracy")
print(p)
```

### Kappa

```{r}
#| label: tbl-train-kappa
#| tbl-cap: 'Training Set Mean Kappa'
#| tbl-pos: 'H'

all_metrics_train |>
  summarize_metrics(metric = "kap") |>
  kbl(booktabs = TRUE, escape = FALSE) |>
  kable_styling() |>
  add_header_above(c(" " = 3, "Histotypes" = 5)) |>
  column_spec(column = 3, border_right = TRUE) |>
  collapse_rows(columns = 1)
```

```{r}
#| label: fig-train-kappa
#| fig-cap: 'Training Set Mean Kappa'
#| fig-height: 8
#| fig-width: 7

p <- ggplot(
  all_metrics_train |> filter(.metric == "kap"),
  aes(
    x = fct_reorder(wflow, mean_estimate, .desc = TRUE),
    y = mean_estimate,
    ymin = lower,
    ymax = upper,
    color = Algorithms,
    shape = Subsampling
  )
) +
  geom_pointrange() +
  scale_colour_viridis_d(begin = 0,
                         end = 0.9,
                         option = "plasma") +
  facet_wrap2(~ class_group,
              ncol = 1,
              strip = strip_themed(background_x = elem_list_rect(fill = c("grey90", class_palette)))) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  labs(x = "Workflow",
       y = "Kappa",
       title = "Training Set Mean Kappa")
print(p)
```
:::

## Rank Aggregation

Multi-step methods:

- **sequential**: sequential algorithm sequence of subsampling methods and algorithms used are:
  - HGSOC vs. non-HGSOC using upsampling and XGBoost
  - CCOC vs. non-CCOC using SMOTE subsampling and XGBoost
  - ENOC vs. non-ENOC using no subsampling and support vector machine
  - MUOC vs. LGSOC using SMOTE subsampling and random forest
- **two_step**: two-step algorithm sequence of subsampling methods and algorithms used are:
  - HGSOC vs. non-HGSOC using upsampling and XGBoost
  - CCOC vs. ENOC vs. MUOC vs. LGSOC using SMOTE subsampling and support vector machine

We conduct rank aggregation using a two-stage nested approach:

1.  First we rank aggregate the per-class metrics for F1-score, balanced accuracy and kappa.
2.  Then we take the aggregated lists from the three metrics and perform a final rank aggregation.
3.  The top workflows from the final rank aggregation are used for gene optimization in the confirmation set

### Across Classes

```{r}
#| label: per-class-metrics

# Add lower, upper, undefined columns for per-class sequential, two_step
per_class_metrics_seq <- per_class_metrics_seq |>
  mutate(class_group = factor(class_group, levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC"))) |> 
  mutate(
    lower = ifelse(all(is.na(.estimate)), NA, min(.estimate, na.rm = TRUE)),
    upper = ifelse(all(is.na(.estimate)), NA, max(.estimate, na.rm = TRUE)),
    .by = c(class_group, .metric)
  ) |>
  mutate(undefined = case_when(any(is.nan(mean_estimate)) ~ "all", any(is.na(.estimate)) ~ "some", .default = "none"),
         .by = .metric) |>
  add_column(wflow = "sequential", .before = 1)

per_class_metrics_two_step <- per_class_metrics_two_step |>
  mutate(class_group = factor(class_group, levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC"))) |> 
  mutate(
    lower = ifelse(all(is.na(.estimate)), NA, min(.estimate, na.rm = TRUE)),
    upper = ifelse(all(is.na(.estimate)), NA, max(.estimate, na.rm = TRUE)),
    .by = c(class_group, .metric)
  ) |>
  mutate(undefined = case_when(any(is.nan(mean_estimate)) ~ "all", any(is.na(.estimate)) ~ "some", .default = "none"),
         .by = .metric) |>
  add_column(wflow = "two_step", .before = 1)

# Combine all per-class metrics
per_class_metrics <- bind_rows(all_metrics_train,
                               per_class_metrics_seq,
                               per_class_metrics_two_step) |>
  filter(class_group != "Overall") |>
  droplevels()

# Keep only workflows that predicted at least one case in each class
per_class_metrics_comp <- per_class_metrics |> 
  distinct(pick(-fold_id, -.estimate)) |> 
  select(wflow, .metric, class_group, mean_estimate) |> 
  arrange(class_group) |> 
  pivot_wider(names_from = "class_group", values_from = "mean_estimate") |> 
  drop_na() |> 
  pivot_longer(cols = where(is.numeric),
               names_to = "class_group",
               values_to = "mean_estimate")
```

::: {#rank-agg-metrics .panel-tabset .nav-pills}
#### F1-Score

```{r}
#| label: tbl-rank-agg-f1
#| tbl-cap: 'F1-Score Rank Aggregation Summary'

# Select ranking metric
per_class_f1 <- filter(per_class_metrics_comp, .metric == "f_meas")

# Rank metric
wflow_ranks_f1 <- per_class_f1 |> 
  mutate(rank = factor(row_number(-mean_estimate)), .by = class_group) |> 
  arrange(rank) |> 
  pivot_wider(id_cols = class_group,
              names_from = "rank",
              values_from = "wflow") |> 
  column_to_rownames("class_group") |> 
  as.matrix()

# Rank aggregation of metrics using genetic algorithm
wflow_rank_agg_f1 <- RankAggreg(
  x = wflow_ranks_f1,
  k = ncol(wflow_ranks_f1),
  method = "GA",
  seed = 2025,
  verbose = FALSE,
  maxIter = 1e4
) |> 
  pluck("top.list") |> 
  enframe(name = "Rank", value = "Workflow")

# Metric summary with rank aggregation
f1_summary <- per_class_f1 |>
  rename(Workflow = wflow) |>
  mutate(mean_estimate = round(mean_estimate, digits = 3)) |>
  inner_join(wflow_rank_agg_f1, by = "Workflow") |>
  pivot_wider(id_cols = c(Workflow, Rank),
              names_from = class_group,
              values_from = mean_estimate) |> 
  arrange(Rank)

# Interactive table showing metrics used in rank aggregation
datatable(
  f1_summary,
  options = list(
    scrollX = TRUE,
    fixedColumns = TRUE,
    columnDefs = list(
      list(
        targets = 1,
        render = JS("$.fn.dataTable.render.ellipsis( 10 )")
      ),
      list(type = "natural", targets = 0)
    ),
    pageLength = 50
  ), 
  rownames = FALSE,
  filter = "top",
  autoHideNavigation = TRUE,
  extensions = "FixedColumns",
  plugins = c("ellipsis", "natural")
)
```

#### Balanced Accuracy

```{r}
#| label: tbl-rank-agg-bal-acc
#| tbl-cap: 'Balanced Accuracy Rank Aggregation Summary'

# Select ranking metric
per_class_bal_acc <- filter(per_class_metrics_comp, .metric == "bal_accuracy")

# Rank metric
wflow_ranks_bal_acc <- per_class_bal_acc |>
  mutate(rank = factor(row_number(-mean_estimate)), .by = class_group) |>
  arrange(rank) |>
  pivot_wider(id_cols = class_group,
              names_from = "rank",
              values_from = "wflow") |>
  column_to_rownames("class_group") |>
  as.matrix()

# Rank aggregation of metrics using genetic algorithm
wflow_rank_agg_bal_acc <- RankAggreg(
  x = wflow_ranks_bal_acc,
  k = ncol(wflow_ranks_bal_acc),
  method = "GA",
  seed = 2025,
  verbose = FALSE,
  maxIter = 1e5
) |> 
  pluck("top.list") |> 
  enframe(name = "Rank", value = "Workflow")

# Metric summary with rank aggregation
bal_acc_summary <- per_class_bal_acc |>
  rename(Workflow = wflow) |>
  mutate(mean_estimate = round(mean_estimate, digits = 3)) |>
  inner_join(wflow_rank_agg_bal_acc, by = "Workflow") |>
  pivot_wider(id_cols = c(Workflow, Rank),
              names_from = class_group,
              values_from = mean_estimate) |> 
  arrange(Rank)

# Interactive table showing metrics used in rank aggregation
datatable(
  bal_acc_summary,
  options = list(
    scrollX = TRUE,
    fixedColumns = TRUE,
    columnDefs = list(
      list(
        targets = 1,
        render = JS("$.fn.dataTable.render.ellipsis( 10 )")
      ),
      list(type = "natural", targets = 0)
    ),
    pageLength = 50
  ), 
  rownames = FALSE,
  filter = "top",
  autoHideNavigation = TRUE,
  extensions = "FixedColumns",
  plugins = c("ellipsis", "natural")
)
```

#### Kappa

```{r}
#| label: tbl-rank-agg-kap
#| tbl-cap: 'Kappa Rank Aggregation Summary'

# Select ranking metric
per_class_kap <- filter(per_class_metrics_comp, .metric == "kap")

# Rank metric
wflow_ranks_kap <- per_class_kap |>
  mutate(rank = factor(row_number(-mean_estimate)), .by = class_group) |>
  arrange(rank) |>
  pivot_wider(id_cols = class_group,
              names_from = "rank",
              values_from = "wflow") |>
  column_to_rownames("class_group") |>
  as.matrix()

# Rank aggregation of metrics using genetic algorithm
wflow_rank_agg_kap <- RankAggreg(
  x = wflow_ranks_kap,
  k = ncol(wflow_ranks_kap),
  method = "GA",
  seed = 2025,
  verbose = FALSE,
  maxIter = 1e4
) |> 
  pluck("top.list") |> 
  enframe(name = "Rank", value = "Workflow")

# Metric summary with rank aggregation
kap_summary <- per_class_kap |>
  rename(Workflow = wflow) |>
  mutate(mean_estimate = round(mean_estimate, digits = 3)) |>
  inner_join(wflow_rank_agg_kap, by = "Workflow") |>
  pivot_wider(id_cols = c(Workflow, Rank),
              names_from = class_group,
              values_from = mean_estimate) |> 
  arrange(Rank)

# Interactive table showing metrics used in rank aggregation
datatable(
  kap_summary,
  options = list(
    scrollX = TRUE,
    fixedColumns = TRUE,
    columnDefs = list(
      list(
        targets = 1,
        render = JS("$.fn.dataTable.render.ellipsis( 10 )")
      ),
      list(type = "natural", targets = 0)
    ),
    pageLength = 50
  ), 
  rownames = FALSE,
  filter = "top",
  autoHideNavigation = TRUE,
  extensions = "FixedColumns",
  plugins = c("ellipsis", "natural")
)
```
:::

### Across Metrics

```{r}
#| label: tbl-rank-agg-comp-metrics
#| tbl-cap: 'Rank Aggregation Comparison of Metrics Used in Training Set'
#| tbl-pos: 'H'

rank_agg_metrics <- list(F1 = wflow_rank_agg_f1,
                         `Balanced Accuracy` = wflow_rank_agg_bal_acc,
                         Kappa = wflow_rank_agg_kap) |>
  bind_rows(.id = "Metric") |>
  pivot_wider(names_from = "Metric", values_from = "Workflow")

rank_agg_metrics |> 
  kbl(booktabs = TRUE, linesep = "") |> 
  kable_styling(full_width = FALSE)
```

```{r}
#| label: tbl-rank-agg-final
#| tbl-cap: 'Top 5 Workflows from Final Rank Aggregation'
#| tbl-pos: 'H'

# Rank aggregation of aggregated metrics using GA
wflow_ranks_metrics <- rank_agg_metrics |> 
  drop_na() |> 
  pivot_longer(cols = where(is.character), names_to = "Metric", values_to = "Workflow") |> 
  pivot_wider(names_from = Rank, values_from = Workflow) |> 
  column_to_rownames("Metric") |> 
  as.matrix()

# Take top 5 workflows
wflow_rank_agg_metrics <- RankAggreg(
  x = wflow_ranks_metrics,
  k = 5,
  method = "GA",
  seed = 2025,
  verbose = FALSE
) |>
  pluck("top.list") |>
  enframe(name = "Rank", value = "Workflow")

# Number of top workflows
n_wflow_top <- nrow(wflow_rank_agg_metrics)

wflow_rank_agg_metrics |> 
  kbl(booktabs = TRUE, linesep = "") |> 
  kable_styling(full_width = FALSE)
```

### Top Workflows

We look at the per-class evaluation metrics of the top `r n_wflow_top` workflows.

```{r}
#| label: tbl-metrics-top
#| tbl-cap: "Top Workflow Per-Class Evaluation Metrics"

metrics_top <- per_class_metrics |> 
  distinct(pick(-fold_id, -.estimate)) |> 
  rename(Workflow = wflow) |> 
  inner_join(wflow_rank_agg_metrics, by = "Workflow") |> 
  mutate(
    Workflow = Workflow |>
      fct_reorder(Rank) |>
      fct_recode(
        Sequential = "sequential",
        `2-STEP` = "two_step",
        `Up-RF` = "up_rf",
        `SMOTE-SVM` = "smote_svm",
        `Hybrid-XGB` = "hybrid_xgb"
      ), 
    .metric = recode_values(
      .metric,
      "accuracy" ~ "Accuracy",
      "sensitivity" ~ "Sensitivity",
      "specificity" ~ "Specificity",
      "f_meas" ~ "F1-Score",
      "bal_accuracy" ~ "Balanced Accuracy",
      "kap" ~ "Kappa",
      ptype = factor(
        levels = c(
          "Accuracy",
          "Sensitivity",
          "Specificity",
          "F1-Score",
          "Balanced Accuracy",
          "Kappa"
        )
      )
    )
  ) |> 
  drop_na(.metric) |> 
  arrange(Rank)

metrics_top_df <- metrics_top |>
  select(Metric = .metric, Workflow, mean_estimate, lower, upper, class_group) |>
  mutate(across(where(is.numeric), ~ round(., digits = 2))) |>
  mutate(Estimate = paste0(mean_estimate, " (", lower, ", ", upper, ")"),
         .keep = "unused") |> 
  arrange(Metric, class_group) |> 
  pivot_wider(names_from = "class_group", values_from = "Estimate")

metrics_top_df |> 
  kbl(booktabs = TRUE, linesep = "") |> 
  kable_styling(full_width = FALSE,
                latex_options = "scale_down") |> 
  collapse_rows(columns = 1) |> 
  add_header_above(c(" " = 2, "Histotypes" = 5))
```

```{r}
#| label: fig-top-wflows-by-all-metric
#| fig-cap: !expr paste('Top', n_wflow_top, 'Workflow Per-Class Evaluation Metrics by Metric')
#| fig-height: 7
#| out-width: '100%'

p <-
  ggplot(metrics_top) +
  geom_pointrange(
    aes(
      x = Workflow,
      y = mean_estimate,
      ymin = lower,
      ymax = upper,
      color = class_group
    ),
    position = position_dodge(width = 0.25),
    size = 0.2
  ) +
  scale_color_brewer(palette = "Dark2") + 
  facet_wrap(vars(.metric), ncol = 1, scales = "free_y") +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank()
  ) +
  labs(
    x = "Workflow",
    y = "Metric Value",
    color = "Class",
    title = paste("Top", n_wflow_top, "Workflow Per-Class Evaluation Metrics by Metric")
  )
print(p)
```

```{r}
#| label: tbl-metrics-3-top-ranks
#| tbl-cap: "Top Workflow Per-Class Evaluation Metrics and Ranks"

metrics_3_top_ranks <- bind_rows(
  `F1-Score` = f1_summary,
  `Balanced Accuracy` = bal_acc_summary,
  Kappa = kap_summary,
  .id = "Metric"
) |>
  semi_join(wflow_rank_agg_metrics, by = "Workflow") |>
  mutate(
    Workflow = Workflow |>
      fct_inorder() |>
      fct_recode(
        Sequential = "sequential",
        `2-STEP` = "two_step",
        `Up-RF` = "up_rf",
        `SMOTE-SVM` = "smote_svm",
        `Hybrid-XGB` = "hybrid_xgb"
      )
  )

metrics_3_top_ranks |> 
  select(-Metric) |> 
  kbl(booktabs = TRUE, linesep = "") |> 
  kable_styling(full_width = FALSE) |> 
  pack_rows(
    group_label = "F1-Score",
    start_row = 1,
    end_row = 5,
    label_row_css = "border-bottom: 1px solid; text-align: center;",
    background = "#fce4d6"
  ) |>
  pack_rows(
    group_label = "Balanced Accuracy",
    start_row = 6,
    end_row = 10,
    label_row_css = "border-bottom: 1px solid; text-align: center;",
    background = "#ededed"
  ) |>
  pack_rows(
    group_label = "Kappa",
    start_row = 11,
    end_row = 15,
    label_row_css = "border-bottom: 1px solid; text-align: center;",
    background = "#e2efda"
  )
```

```{r}
#| label: fig-top-wflows-by-three-metrics
#| fig-cap: !expr paste('Top', n_wflow_top, 'Workflow Per-Class Evaluation Metrics by Metric')
#| fig-width: 10
#| fig-height: 6
#| out-width: '100%'

metrics_3_top <- metrics_top |> 
  filter(.metric %in% c("F1-Score", "Balanced Accuracy", "Kappa")) |> 
  mutate(.metric = droplevels(.metric))

p <-
  ggplot(metrics_3_top) +
  geom_pointrange(
    aes(
      x = class_group,
      y = mean_estimate,
      ymin = lower,
      ymax = upper,
      color = Workflow
    ),
    position = position_dodge(width = 0.5),
    size = 0.2
  ) +
  geom_hline(yintercept = 0.8, color = "grey20", alpha = 0.5, linetype = "dashed") +
  scale_color_brewer(palette = "Set1") +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  facet_wrap(vars(.metric), nrow = 1) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(0.01, 0.01),
    legend.justification.inside = c(0, 0)
  ) +
  labs(
    x = "Workflow",
    y = "Metric Value",
    title = paste("Top", n_wflow_top, "Workflow Per-Class Evaluation Metrics by Metric")
  )
print(p)
```

Misclassified cases from a previous step of the sequence of classifiers are not included in subsequent steps of the training set CV folds. Thus, we cannot piece together the test set predictions from the sequential and two-step algorithms to obtain overall metrics.

## Confirmation Set

Now we'd like to see how our best five workflows perform in the confirmation set. The class-specific F1-scores will be used. The top performing method will be selected for gene optimization.

```{r}
#| label: top-models

# Sequential model
mod_seq <- list(all_models_seq,
                seq_data,
                seq_class) |> 
  pmap(~ {
    set.seed(2024)
    ..1 |> fit(data = cbind(..2, class = factor(..3)))
  })

# Two-step model
mod_two_step <- list(all_models_two_step,
                     two_step_data,
                     two_step_class) |> 
  pmap(~ {
    set.seed(2024)
    ..1 |> fit(data = cbind(..2, class = factor(..3)))
  })

# Training data
train_ref <- train_data |>
  mutate(class = factor(train_class, levels = c("CCOC", "ENOC", "HGSOC", "LGSOC", "MUOC")))

# Up-RF model
set.seed(2024)
mod_up_rf <- wflow_up_rf_model |>
  fit(data = train_ref)

# SMOTE-SVM model
set.seed(2024)
mod_smote_svm <- wflow_smote_svm_model |> 
  fit(data = train_ref)

# Hybrid-XGB model
set.seed(2024)
mod_hybrid_xgb <- wflow_hybrid_xgb_model |> 
  fit(data = train_ref)

# Per-class metric set
per_class_mset <-
  metric_set(accuracy, sensitivity, specificity, f_meas, bal_accuracy, kap)
```

```{r}
#| label: tbl-conf-eval
#| tbl-cap: 'Evaluation Metrics on Confirmation Set Models'
#| tbl-pos: 'H'

# Confirmation set overall predictions
conf_pred_overall <- data.frame(FileName = rownames(conf_data),
                                Truth = conf_class) |>
  mutate(
    c(p_seq = mod_seq,
      p_two_step = mod_two_step,
      p_up_rf = list(mod_up_rf),
      p_smote_svm = list(mod_smote_svm),
      p_hybrid_xgb = list(mod_hybrid_xgb)
    ) |> 
      map(~ predict(., conf_data)[[".pred_class"]]) |> 
      bind_cols()
  ) |> 
  rename_with(~ gsub("(.*)\\..*_(.*)", "\\1_\\2", .), where(is.factor)) |> 
  mutate(
    across(matches("p"), as.character),
    Prediction_sequential = case_when(
      !grepl("non", p_seq_s1) ~ p_seq_s1,
      !grepl("non", p_seq_s2) ~ p_seq_s2,
      !grepl("non", p_seq_s3) ~ p_seq_s3,
      .default = p_seq_s4
    ),
    Prediction_two_step = ifelse(!grepl("non", p_two_step_s1),
                                      p_two_step_s1, p_two_step_s2),
    Prediction_up_rf = p_up_rf,
    Prediction_smote_svm = p_smote_svm,
    Prediction_hybrid_xgb = p_hybrid_xgb,
    across(c("Truth", matches("Prediction")), factor)
  ) |> 
  select(-starts_with("p", ignore.case = FALSE)) |> 
  pivot_longer(
    cols = matches("Prediction"),
    names_to = "Method",
    names_prefix = "Prediction_",
    values_to = "Prediction"
  ) |> 
  mutate(across(c(Truth, Prediction),
                ~ factor(.x,
                         levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC")))) |> 
  mutate(Method = fct_inorder(
    recode_values(
      Method,
      "sequential" ~ "Sequential",
      "two_step" ~ "2-STEP",
      "up_rf" ~ "Up-RF",
      "smote_svm" ~ "SMOTE-SVM",
      "hybrid_xgb" ~ "Hybrid-XGB"
    )
  ))

# Confirmation set overall metrics
conf_eval_overall <- conf_pred_overall |>
  summarize(
    Accuracy = accuracy_vec(Truth, Prediction),
    Sensitivity = sensitivity_vec(Truth, Prediction),
    Specificity = specificity_vec(Truth, Prediction),
    `F1-Score` = f_meas_vec(Truth, Prediction),
    `Balanced Accuracy` = bal_accuracy_vec(Truth, Prediction),
    Kappa = kap_vec(Truth, Prediction),
    .by = Method
  ) |>
  pivot_longer(cols = where(is.numeric),
               names_to = "Metric",
               values_to = "Overall")

# Confirmation set per-class metrics
conf_eval_per_class <- conf_pred_overall |> 
  nest(.by = Method) |> 
  mutate(data = map(data, ~ ova_metrics(.x, Truth, Prediction, per_class_mset))) |> 
  unnest(data) |> 
  mutate(
    Metric = recode_values(
      .metric,
      "accuracy" ~ "Accuracy",
      "sensitivity" ~ "Sensitivity",
      "specificity" ~ "Specificity",
      "f_meas" ~ "F1-Score",
      "bal_accuracy" ~ "Balanced Accuracy",
      "kap" ~ "Kappa"
    ),
    .keep = "unused"
  ) |> 
  pivot_wider(
    id_cols = c(Method, Metric),
    names_from = class_group,
    values_from = .estimate
  )

# Combined all metrics
conf_eval <-
  inner_join(conf_eval_overall,
             conf_eval_per_class,
             by = c("Method", "Metric"))
  
conf_eval |> 
  kbl(booktabs = TRUE, linesep = "", digits = 3) |> 
  kable_styling(latex_options = "scale_down") |> 
  collapse_rows(columns = 1) |>  
  add_header_above(c(" " = 3, "Histotypes" = 5))
```

```{r}
#| label: fig-conf-eval
#| fig-cap: 'Evaluation Metrics on Confirmation Set Models'
#| fig-height: 7
#| fig-width: 9

conf_eval_long <- conf_eval |>
  pivot_longer(cols = where(is.double),
               names_to = "Class",
               values_to = "Score") |>
  mutate(Method = fct_rev(Method),
         Metric = fct_inorder(Metric),
         Class = fct_inorder(Class))

ggplot(conf_eval_long) +
  geom_tile(aes(x = Class, y = Method, fill = Score)) +
  geom_text(aes(x = Class, y = Method, label = round(Score, digits = 2)),
            size = 3) +
  facet_wrap(vars(Metric)) +
  scale_fill_viridis_c(option = "plasma",
                       breaks = c(0, 1),
                       limits = c(0, 1),
                       begin = 0.2) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text.x.bottom = element_text(angle = 45, hjust = 1, vjust = 1),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) +
  labs(title = "Evaluation Metrics on Confirmation Set Models")
```

```{r}
#| label: fig-conf-entropy
#| fig-cap: 'Entropy vs. Predicted Probability in Confirmation Set'
#| fig-width: 10
#| fig-height: 6
#| out-width: '100%'

conf_entropy <- data.frame(FileName = rownames(conf_data),
                           Truth = conf_class) |>
  mutate(
    c(p_seq = mod_seq,
      p_two_step = mod_two_step,
      p_up_rf = list(up_rf = mod_up_rf),
      p_smote_svm = list(smote_svm = mod_smote_svm),
      p_hybrid_xgb = list(hybrid_xgb = mod_hybrid_xgb)
  ) |>
      map(~ {
        predict(., conf_data, type = "prob") |>
          rowwise() |>
          mutate(
            prob = max(c_across(where(is.numeric))),
            entropy = entropy::entropy(c_across(matches(".pred")), unit = "log2")
          ) |>
          ungroup()
      }) |>
      list_cbind() |>
      unnest_wider(col = everything(), names_sep =  "/")
  ) |>
  pivot_longer(
    cols = where(is.numeric),
    names_to = c("Method", "Workflow", "Metric"),
    names_pattern = "(.*)\\.(.*)/(.*)",
    values_to = "Value"
  ) |>
  mutate(
    Truth = factor(Truth,
                   levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC")),
    Method = fct_inorder(
      recode_values(
        Method,
        "p_seq" ~ "Sequential",
        "p_two_step" ~ "2-STEP",
        "p_up_rf" ~ "Up-RF",
        "p_smote_svm" ~ "SMOTE-SVM",
        "p_hybrid_xgb" ~ "Hybrid-XGB"
        )
      )
    ) |>
  inner_join(conf_pred_overall, by = join_by(FileName, Truth, Method)) |>
  filter(Metric %in% c("prob", "entropy")) |>
  filter(
    (grepl("Sequential", Method) & (
      Prediction == "HGSOC" & grepl("s1", Workflow) |
        Prediction == "CCOC" & grepl("s2", Workflow) |
        Prediction == "ENOC" & grepl("s3", Workflow) |
        Prediction %in% c("MUOC", "LGSOC") & grepl("s4", Workflow)
    )) |
      grepl("Up-RF", Method) |
      grepl("SMOTE-SVM", Method) |
      grepl("Hybrid-XGB", Method) |
    (grepl("2-STEP", Method) & (
      Prediction == "HGSOC" & grepl("s1", Workflow) |
        Prediction != "HGSOC" & grepl("s2", Workflow)
    ))
  ) |>
  pivot_wider(names_from = Metric, values_from = Value)

p <- ggplot(conf_entropy) +
  geom_point(aes(x = prob, y = entropy, color = Prediction), alpha = 0.5) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
  facet_wrap(vars(Method), ncol = 2) +
  labs(
    x = "Probability",
    y = "Entropy (log base 2)",
    title = "Entropy vs. Predicted Probability in Confirmation Set"
  )
print(p)
```

```{r}
#| label: fig-conf-metrics-gene-opt
#| fig-cap: 'Gene Optimized Workflows Per-Class Metrics in Confirmation Set'
#| fig-width: 10
#| fig-height: 6
#| out-width: '100%'

conf_metrics_top <- conf_eval_per_class |>
  pivot_longer(
    cols = where(is.numeric),
    names_to = "Class",
    names_ptypes = list(Class = factor()),
    values_to = "Value"
  ) |>
  filter(Metric %in% c("F1-Score", "Balanced Accuracy", "Kappa")) |> 
  mutate(Metric = fct_inorder(Metric))

p <- ggplot(conf_metrics_top) +
  geom_col(
    aes(x = Class, y = Value, fill = Method),
    position = position_dodge()
  ) +
  geom_hline(yintercept = 0.8, color = "grey20", alpha = 0.5, linetype = "dashed") +
  scale_fill_brewer(palette = "Set1") +
  scale_y_continuous(breaks = seq(0, 1, 0.2)) +
  facet_wrap(vars(Metric), nrow = 1) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    legend.position = "bottom"
  ) +
  labs(
    y = "Metric Value",
    title = paste("Gene-Optimized Workflows Per-Class Metrics in Confirmation Set")
  )
print(p)
```

```{r}
#| label: fig-conf-conf-mat
#| fig-cap: !expr get_plot_title()
#| fig-height: 9
#| fig-width: 8
#| out-width: '100%'

conf_conf_mat <- conf_pred_overall |>
  nest(.by = Method) |>
  deframe() |>
  imap(~ plot_conf_mat(data = .x, title = .y, cols = class_palette)) |>
  wrap_plots(nrow = 3) +
  plot_annotation(title = "Confusion Matrices for Confirmation Set Models", tag_levels = "A")

print(conf_conf_mat)
```

::: {#conf-roc-curves .panel-tabset .nav-pills}
```{r}
#| label: roc-curve-setup

conf_data_seq <- list(conf_data,
                      conf_data[conf_class != "HGSOC",],
                      conf_data[!conf_class %in% c("HGSOC", "CCOC"),],
                      conf_data[!conf_class %in% c("HGSOC", "CCOC", "ENOC"),])

conf_class_seq <- list(
  fct_other(conf_class, keep = "HGSOC", other_level = "non-HGSOC"),
  fct_other(conf_class[conf_class != "HGSOC"],  keep = "CCOC", other_level = "non-CCOC"),
  fct_other(conf_class[!conf_class %in% c("HGSOC", "CCOC")],  keep = "ENOC", other_level = "non-ENOC"),
  factor(conf_class[!conf_class %in% c("HGSOC", "CCOC", "ENOC")])
)

conf_data_two_step <- list(conf_data,
                           conf_data[conf_class != "HGSOC", ])

conf_class_two_step <-
  list(factor(ifelse(conf_class == "HGSOC", "HGSOC", "non-HGSOC")),
       factor(conf_class[conf_class != "HGSOC"]))

class_groups_seq <-
  set_names(class_palette, paste0("(?<!non_)", c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC"))) |>
  imap_chr(~ paste0(
    "<span style = 'color:",
    .x,
    ";'>",
    gsub("(?<!non_)", "", .y, fixed = TRUE),
    "</span>"
  )) |>
  str_replace_all(string = conf_class_seq |> 
                    map(levels) |> 
                    map_at(4, rev) |> 
                    map_chr(~ gsub("-", "_", paste(., collapse = " vs. "))),
                  pattern = _)

class_groups_two_step <- 
  set_names(class_palette, paste0("(?<!non_)", c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC"))) |>
  imap_chr(~ paste0(
    "<span style = 'color:",
    .x,
    ";'>",
    gsub("(?<!non_)", "", .y, fixed = TRUE),
    "</span>"
  )) |>
  str_replace_all(string = conf_class_two_step |> 
                    map(levels) |> 
                    map_at(2, \(x) x[c(1, 2, 4, 3)]) |> 
                    map_chr(~ gsub("-", "_", paste(., collapse = " vs. "))),
                  pattern = _)
```

### Sequential

```{r}
#| label: fig-conf-roc-seq
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 7
#| out-width: '100%'

roc_curve_seq <-
  list(mod_seq, conf_data_seq, conf_class_seq, class_groups_seq) |>
  pmap(~ plot_roc_curve(
    model = ..1,
    data = ..2,
    class = ..3,
    title = ..4
  )) |>
  wrap_plots(widths = c(1, -1)) +
  plot_annotation(title = "ROC Curves for Sequential Model in Confirmation Set", tag_levels = "A")

print(roc_curve_seq)
```

### 2-STEP

```{r}
#| label: fig-conf-roc-two-step
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 9
#| out-width: '100%'

roc_curve_two_step <-
  list(mod_two_step,
       conf_data_two_step,
       conf_class_two_step,
       class_groups_two_step) |>
  pmap(~ plot_roc_curve(
    model = ..1,
    data = ..2,
    class = ..3,
    title = ..4
  )) |>
  wrap_plots(widths = c(1, -1)) +
  plot_annotation(title = "ROC Curves for 2-STEP Model in Confirmation Set", tag_levels = "A")

print(roc_curve_two_step)
```

### Up-RF

```{r}
#| label: fig-conf-roc-up-rf
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_roc_curve(
  model = mod_up_rf,
  data = conf_data,
  class = conf_class,
  title = "ROC Curve for Up-RF Model in Confirmation Set",
  cols = class_palette
)
```

### SMOTE-SVM

```{r}
#| label: fig-conf-roc-smote-svm
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_roc_curve(
  model = mod_smote_svm,
  data = conf_data,
  class = conf_class,
  title = "ROC Curve for SMOTE-SVM Model in Confirmation Set",
  cols = class_palette
)
```

### Hybrid-XGB

```{r}
#| label: fig-conf-roc-hybrid-xgb
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_roc_curve(
  model = mod_hybrid_xgb,
  data = conf_data,
  class = conf_class,
  title = "ROC Curve for Hybrid-XGB Model in Confirmation Set",
  cols = class_palette
)
```
:::

```{r}
#| label: conf-de-rank

# Candidate genes are the ones in the overlap set but not in PrOTYPE or SPOT
candidates <- c("C10orf116", "GAD1", "TPX2", "KGFLP2", "EGFL6", "KLK7", "PBX1",
                "LIN28B", "TFF3", "MUC5B", "FUT3", "STC1", "BCL2", "PAX8", "GCNT3",
                "GPR64", "ADCYAP1R1", "IGKC", "BRCA1", "IGJ", "TFF1", "MET",
                "CYP2C18", "CYP4B1", "SLC3A1", "EPAS1", "HNF1B", "IL6", "ATP5G3",
                "DKK4", "SENP8", "CAPN2", "C1orf173", "CPNE8", "IGFBP1", "WT1",
                "TP53", "SEMA6A", "SERPINA5", "ZBED1", "TSPAN8", "SCGB1D2", "LGALS4",
                "MAP1LC3A")

# LGSOC differential gene expression analysis in confirmation set
res_conf_lgsoc <- gene_rank_de(
  data = cs3,
  preds = conf_pred_overall,
  method = "Hybrid-XGB",
  class = "LGSOC",
  candidates = candidates
)

# ENOC differential gene expression analysis in confirmation set
res_conf_enoc <- gene_rank_de(
  data = cs3,
  preds = conf_pred_overall,
  method = "Hybrid-XGB",
  class = "ENOC",
  candidates = candidates
)

# Gene rank via differential expression in confirmation set
conf_de_rank <-
  bind_rows(LGSOC = res_conf_lgsoc, ENOC = res_conf_enoc, .id = "class") |>
  pivot_wider(names_from = "class", values_from = "Rank") |>
  mutate(Variable = Gene,
         Rank = row_number(rowMeans(pick(LGSOC, ENOC))),
         .keep = "unused") |>
  arrange(Rank)
saveRDS(conf_de_rank, here("data/conf_de_rank.rds"))
```

## Gene Optimization

From @fig-conf-eval, we see that both Hybrid-XGB and SMOTE-SVM have the highest overall F1-Score and are relatively better at predicting the rarest histotype LGSOC (sensitivity = 0.42). Thus we choose both of these two workflows for gene optimization in the confirmation set. The optimal number of genes is determined by the highest average F1-Score across classes, including the overall metric in the average. We use an F1-score that is averaged across cross-validation folds (5) and class groups (6: Overall, HGSOC, CCOC, ENOC, MUOC, LGSOC) to compare performance between different number of genes selected.

### Hybrid-XGB

```{r}
#| label: fig-gene-hybrid-xgb
#| fig-cap: 'Gene Optimization for Hybrid-XGB Classifier using Averaged F1-Score'
#| fig-height: 2
#| fig-width: 5
#| out-width: '100%'

gene_hybrid_xgb_names <- all_vi_train |> 
  filter(wflow == "hybrid_xgb") |> 
  rowid_to_column("Genes") |> 
  select(Genes, Name = Variable) |> 
  add_row(Genes = 0L, Name = "Base", .before = 1) |> 
  slice_min(order_by = Genes, n = -1)

dat_gene_hybrid_xgb <- gene_opt_all_metrics_conf |> 
  filter(Workflow == "hybrid_xgb", .metric == "f_meas") |> 
  inner_join(gene_hybrid_xgb_names, by = "Genes") |> 
  mutate(
    min_estimate = min(.estimate, na.rm = TRUE),
    max_estimate = max(.estimate, na.rm = TRUE),
    .by = c(Genes, class_group)
  ) |>
  summarize(
    Name = unique(Name),
    mean_estimate = mean(mean_estimate),
    min_estimate = mean(min_estimate),
    max_estimate = mean(max_estimate),
    .by = Genes
  ) |> 
  mutate(Optimal = ifelse(Genes == Genes[which.max(mean_estimate)], TRUE, FALSE))

p_gene_hybrid_xgb <- 
  ggplot(dat_gene_hybrid_xgb, aes(text = Name)) +
  geom_pointrange(
    aes(
      x = Genes,
      y = mean_estimate,
      ymin = min_estimate,
      ymax = max_estimate,
      color = Optimal
    ),
    show.legend = FALSE
  ) +
  scale_color_manual(values = c("black", "red")) +
  theme_bw() +
  labs(
    x = "Genes Added",
    y = "Averaged F1-Score",
    title = "Gene Optimziation for Hybrid-XGB",
    color = NULL
  )
ggplotly(p_gene_hybrid_xgb, width = 600, height = 600) |> 
  layout(showlegend = FALSE)

n_genes_hybrid_xgb <- dat_gene_hybrid_xgb |> 
  filter(Optimal) |> 
  pull(Genes) |> 
  unique()
genes_add_hybrid_xgb <- gene_hybrid_xgb_names |> 
  filter(Genes > 0L) |> 
  slice_min(order_by = Genes, n = n_genes_hybrid_xgb) |> 
  pull(Name)
opt_genes_hybrid_xgb <- c(overlap_all, genes_add_hybrid_xgb)
```

In the Hybrid-XGB classifier, the optimal number of genes is highlighted in red in @fig-gene-hybrid-xgb. Hence the optimal number of total genes used will be n=`r length(overlap_all)`+`r n_genes_hybrid_xgb`=`r length(opt_genes_hybrid_xgb)`.

The gene profile of the optimal set of genes used is displayed in @tbl-gene-opt-hybrid-xgb. Base genes in the PrOTYPE and SPOT sets are annotated with green circles, and the added genes are annotated with yellow circles. The added genes are: `r str_flatten_comma(genes_add_hybrid_xgb, last = " and ")`. Unused genes are annotated with red crosses.

```{r}
#| label: tbl-gene-opt-hybrid-xgb
#| tbl-cap: 'Gene Profile of Optimal Set in Hybrid-XGB Workflow'
#| tbl-pos: 'H'

candidates_all <- gene_hybrid_xgb_names |>
  filter(Genes > 0) |>
  pull(Name)
unused_genes_hybrid_xgb <- gene_hybrid_xgb_names |>
  filter(Genes > 0) |>
  slice_max(order_by = Genes, n = -n_genes_hybrid_xgb) |> 
  arrange(Genes) |> 
  pull(Name)
gene_order_hybrid_xgb <- c(opt_genes_hybrid_xgb, unused_genes_hybrid_xgb)

gene_dist_hybrid_xgb <-
  tibble(
    Genes = gene_order_hybrid_xgb,
    Set = ifelse(Genes %in% overlap_all, "Base", "Candidates"),
    PrOTYPE = ifelse(Genes %in% overlap_PrOTYPE, symbol$tick, ""),
    SPOT = ifelse(Genes %in% overlap_SPOT, symbol$tick, ""),
    `Optimal Set` = if_else(
      Genes %in% opt_genes_hybrid_xgb,
      symbol$circle_filled,
      symbol$circle_cross
    ) |>
      cell_spec(
        color = case_when(
          Genes %in% overlap_all ~ "green",
          Genes %in% opt_genes_hybrid_xgb ~ "#8B8000",
          .default = "#FF0000"
        )
      ),
    `Candidate Rank` = ifelse(Genes %in% overlap_all, "", match(Genes, candidates_all)
    )
  ) |>
  relocate(Set, .before = Genes)

gene_dist_hybrid_xgb |> 
  kbl(booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      escape = FALSE) |> 
  kable_styling(full_width = FALSE) |> 
  collapse_rows(columns = 1)
```

### SMOTE-SVM

```{r}
#| label: fig-gene-smote-svm
#| fig-cap: 'Gene Optimization for SMOTE-SVM Classifier using Averaged F1-Score'
#| fig-height: 2
#| fig-width: 5
#| out-width: '100%'

gene_smote_svm_names <- all_vi_train |> 
  filter(wflow == "smote_svm") |> 
  rowid_to_column("Genes") |> 
  select(Genes, Name = Variable) |> 
  add_row(Genes = 0L, Name = "Base", .before = 1) |> 
  slice_min(order_by = Genes, n = -1)

dat_gene_smote_svm <- gene_opt_all_metrics_conf |> 
  filter(Workflow == "smote_svm", .metric == "f_meas") |> 
  inner_join(gene_smote_svm_names, by = "Genes") |> 
  mutate(
    min_estimate = min(.estimate, na.rm = TRUE),
    max_estimate = max(.estimate, na.rm = TRUE),
    .by = c(Genes, class_group)
  ) |>
  summarize(
    Name = unique(Name),
    mean_estimate = mean(mean_estimate),
    min_estimate = mean(min_estimate),
    max_estimate = mean(max_estimate),
    .by = Genes
  ) |> 
  mutate(Optimal = ifelse(Genes == Genes[which.max(mean_estimate)], TRUE, FALSE))

p_gene_smote_svm <- 
  ggplot(dat_gene_smote_svm, aes(text = Name)) +
  geom_pointrange(
    aes(
      x = Genes,
      y = mean_estimate,
      ymin = min_estimate,
      ymax = max_estimate,
      color = Optimal
    ),
    show.legend = FALSE
  ) +
  scale_color_manual(values = c("black", "red")) +
  theme_bw() +
  labs(
    x = "Genes Added",
    y = "Averaged F1-Score",
    title = "Gene Optimziation for SMOTE-SVM",
    color = NULL
  )
ggplotly(p_gene_smote_svm, width = 600, height = 600) |> 
  layout(showlegend = FALSE)

n_genes_smote_svm <- dat_gene_smote_svm |> 
  filter(Optimal) |> 
  pull(Genes) |> 
  unique()
genes_add_smote_svm <- gene_smote_svm_names |> 
  filter(Genes > 0L) |> 
  slice_min(order_by = Genes, n = n_genes_smote_svm) |> 
  pull(Name)
opt_genes_smote_svm <- c(overlap_all, genes_add_smote_svm)
```

In the SMOTE-svm classifier, the optimal number of genes is achieved at the highest averaged F1-score with `r n_genes_smote_svm` genes added, highlighted in red in @fig-gene-smote-svm. Hence the optimal number of total genes used will be n=`r length(overlap_all)`+`r n_genes_smote_svm`=`r length(opt_genes_smote_svm)`.

The gene profile of the optimal set of genes used is displayed in @tbl-gene-opt-smote-svm. Base genes in the PrOTYPE and SPOT sets are annotated with green circles, and the added genes are annotated with yellow circles. The added genes are: `r str_flatten_comma(genes_add_smote_svm, last = " and ")`. Unused genes are annotated with red crosses.

```{r}
#| label: tbl-gene-opt-smote-svm
#| tbl-cap: 'Gene Profile of Optimal Set in SMOTE-SVM Workflow'
#| tbl-pos: 'H'

candidates_all <- gene_smote_svm_names |>
  filter(Genes > 0) |>
  pull(Name)
unused_genes_smote_svm <- gene_smote_svm_names |>
  filter(Genes > 0) |>
  slice_max(order_by = Genes, n = -n_genes_smote_svm) |> 
  arrange(Genes) |> 
  pull(Name)
gene_order_smote_svm <- c(opt_genes_smote_svm, unused_genes_smote_svm)

gene_dist_smote_svm <-
  tibble(
    Genes = gene_order_smote_svm,
    Set = ifelse(Genes %in% overlap_all, "Base", "Candidates"),
    PrOTYPE = ifelse(Genes %in% overlap_PrOTYPE, symbol$tick, ""),
    SPOT = ifelse(Genes %in% overlap_SPOT, symbol$tick, ""),
    `Optimal Set` = if_else(
      Genes %in% opt_genes_smote_svm,
      symbol$circle_filled,
      symbol$circle_cross
    ) |>
      cell_spec(
        color = case_when(
          Genes %in% overlap_all ~ "green",
          Genes %in% opt_genes_smote_svm ~ "#8B8000",
          .default = "#FF0000"
        )
      ),
    `Candidate Rank` = ifelse(Genes %in% overlap_all, "", match(Genes, candidates_all)
    )
  ) |>
  relocate(Set, .before = Genes)

gene_dist_smote_svm |> 
  kbl(booktabs = TRUE,
      longtable = TRUE,
      linesep = "",
      escape = FALSE) |> 
  kable_styling(full_width = FALSE) |> 
  collapse_rows(columns = 1)
```

### Gene List Comparisons in Confirmation Set

We train the Hybrid-XGB and SMOTE-SVM workflows using the base and optimal gene lists in the training set. The models are evaluated on the confirmation set. Overall and per-class results are shown in @tbl-gene-list-comps-conf. The gene lists are:

1.  Base (n=28): among the overlapping genes, the base set from the PrOTYPE and SPOT lists

2.  Optimal (n=47, 69): among the overlapping genes, the base set plus the additional number of genes that result in the optimal value for a selected evaluation metric, as assessed in @fig-gene-hybrid-xgb and @fig-gene-smote-svm

```{r}
#| label: tbl-gene-list-comps-conf
#| tbl-cap: 'Model Comparisons using Different Gene Lists in Confirmation Set'
#| tbl-pos: 'H'

## Hybrid-XGB
# Optimal workflow
set.seed(2024)
wflow_hybrid_xgb_opt <- wflow_hybrid_xgb_model |>
  pluck("pre", "actions", "recipe", "recipe") |>
  modify_at(c("var_info", "term_info"),
            \(x) x |>
              filter(variable %in% c(opt_genes_hybrid_xgb, "class")) |>
              arrange(match(variable, gene_order_hybrid_xgb))) |>
  update_recipe(x = wflow_hybrid_xgb_model, recipe = _)

# Optimal model
set.seed(2024)
mod_hybrid_xgb_opt <- wflow_hybrid_xgb_opt |>
  fit(data = train_ref)

# Base workflow
set.seed(2024)
wflow_hybrid_xgb_base <- wflow_hybrid_xgb_model |>
  pluck("pre", "actions", "recipe", "recipe") |>
  modify_at(c("var_info", "term_info"),
            \(x) x |>
              filter(variable %in% c(overlap_all, "class")) |>
              arrange(match(variable, gene_order_hybrid_xgb))) |>
  update_recipe(x = wflow_hybrid_xgb_model, recipe = _)

# Base model
set.seed(2024)
mod_hybrid_xgb_base <- wflow_hybrid_xgb_base |>
  fit(data = train_ref)

## SMOTE-SVM
# Optimal workflow
set.seed(2024)
wflow_smote_svm_opt <- wflow_smote_svm_model |>
  pluck("pre", "actions", "recipe", "recipe") |>
  modify_at(c("var_info", "term_info"),
            \(x) x |>
              filter(variable %in% c(opt_genes_smote_svm, "class")) |>
              arrange(match(variable, gene_order_smote_svm))) |>
  update_recipe(x = wflow_smote_svm_model, recipe = _)

# Optimal model
set.seed(2024)
mod_smote_svm_opt <- wflow_smote_svm_opt |>
  fit(data = train_ref)

# Base workflow
set.seed(2024)
wflow_smote_svm_base <- wflow_smote_svm_model |>
  pluck("pre", "actions", "recipe", "recipe") |>
  modify_at(c("var_info", "term_info"),
            \(x) x |>
              filter(variable %in% c(overlap_all, "class")) |>
              arrange(match(variable, gene_order_smote_svm))) |>
  update_recipe(x = wflow_smote_svm_model, recipe = _)

# Base model
set.seed(2024)
mod_smote_svm_base <- wflow_smote_svm_base |>
  fit(data = train_ref)

# Confirmation set overall predictions
conf_pred_overall <- data.frame(FileName = rownames(conf_data),
                                Truth = conf_class) |>
  mutate(
    Prediction_hybrid_xgb_opt = predict(mod_hybrid_xgb_opt, conf_data)[[".pred_class"]],
    Prediction_hybrid_xgb_base = predict(mod_hybrid_xgb_base, conf_data)[[".pred_class"]],
    Prediction_smote_svm_opt = predict(mod_smote_svm_opt, conf_data)[[".pred_class"]],
    Prediction_smote_svm_base = predict(mod_smote_svm_base, conf_data)[[".pred_class"]],
    across(c("Truth", matches("Prediction")), factor)
  ) |> 
  pivot_longer(
    cols = matches("Prediction"),
    names_to = "Method",
    names_prefix = "Prediction_",
    values_to = "Prediction"
  ) |> 
  mutate(
    across(c(Truth, Prediction), ~ factor(.x, levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC"))), 
    Method = fct_inorder(
      recode_values(
        Method,
        "hybrid_xgb_opt" ~ "Hybrid-XGB, Optimal",
        "hybrid_xgb_base" ~ "Hybrid-XGB, Base",
        "smote_svm_opt" ~ "SMOTE-SVM, Optimal",
        "smote_svm_base" ~ "SMOTE-SVM, Base",
      )
    ))

# Confirmation set overall metrics
conf_eval_overall <- conf_pred_overall |>
  summarize(
    Accuracy = accuracy_vec(Truth, Prediction),
    Sensitivity = sensitivity_vec(Truth, Prediction),
    Specificity = specificity_vec(Truth, Prediction),
    `F1-Score` = f_meas_vec(Truth, Prediction),
    `Balanced Accuracy` = bal_accuracy_vec(Truth, Prediction),
    Kappa = kap_vec(Truth, Prediction),
    .by = Method
  ) |> 
  pivot_longer(
    cols = where(is.numeric),
    names_to = "Metric",
    values_to = "Overall"
  )

# Confirmation set per-class metrics
conf_eval_per_class <- conf_pred_overall |>
  nest(.by = Method) |> 
  mutate(data = map(data, ~ ova_metrics(.x, Truth, Prediction, per_class_mset))) |> 
  unnest(data) |> 
  mutate(
    Metric = recode_values(
      .metric,
      "accuracy" ~ "Accuracy",
      "sensitivity" ~ "Sensitivity",
      "specificity" ~ "Specificity",
      "f_meas" ~ "F1-Score",
      "bal_accuracy" ~ "Balanced Accuracy",
      "kap" ~ "Kappa"
    ),
    .keep = "unused"
  ) |>
  pivot_wider(
    id_cols = c(Method, Metric),
    names_from = class_group,
    values_from = .estimate
  )

# Combined all metrics
conf_eval <-
  inner_join(conf_eval_overall, conf_eval_per_class, by = c("Method", "Metric"))

conf_eval |> 
  kbl(booktabs = TRUE, linesep = "", digits = 3) |>
  kable_styling() |> 
  collapse_rows(columns = 1) |> 
  add_header_above(c(" " = 3, "Histotypes" = 5))
```

```{r}
#| label: fig-gene-list-comps-conf
#| fig-cap: 'Gene List Comparisons of Evaluation Metrics in Confirmation Set'
#| fig-width: 10
#| out-width: '100%'

conf_eval_long <- conf_eval |>
  pivot_longer(cols = where(is.double),
               names_to = "Class",
               values_to = "Score") |>
  mutate(Method = fct_rev(Method),
         Metric = fct_inorder(Metric),
         Class = fct_inorder(Class))

ggplot(conf_eval_long) +
  geom_tile(aes(x = Class, y = Method, fill = Score)) +
  geom_text(aes(x = Class, y = Method, label = round(Score, digits = 2)),
            size = 3) +
  facet_wrap(vars(Metric)) +
  scale_fill_viridis_c(option = "plasma",
                       breaks = c(0, 1),
                       limits = c(0, 1),
                       begin = 0.2) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text.x.bottom = element_text(angle = 45, hjust = 1, vjust = 1),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) +
  labs(title = "Gene List Comparisons of Evaluation Metrics in Confirmation Set")
```

## Validation Set

From the results in @tbl-gene-list-comps-conf and @fig-gene-list-comps-conf, we see that the Hybrid-XGB, optimal workflow as the highest overall F1-Score and balanced accuracy. Thus, we choose the Hybrid-XGB model trained on the training set for the all overlap, optimal, and base gene lists, and evaluate performance in the validation set.

### Evaluation Metrics

```{r}
#| label: tbl-val-eval
#| tbl-cap: 'Evaluation Metrics on Training Set Models in Validation Set'
#| tbl-pos: 'H'

# Validation set overall predictions
val_pred_overall <- data.frame(FileName = rownames(val_data),
                               Truth = val_class) |>
  mutate(
    Prediction_hybrid_xgb_all = predict(mod_hybrid_xgb, val_data)[[".pred_class"]], 
    Prediction_hybrid_xgb_opt = predict(mod_hybrid_xgb_opt, val_data)[[".pred_class"]],
    Prediction_hybrid_xgb_base = predict(mod_hybrid_xgb_base, val_data)[[".pred_class"]],
    across(c("Truth", matches("Prediction")), factor)
  ) |> 
  pivot_longer(
    cols = matches("Prediction"),
    names_to = "Method",
    names_prefix = "Prediction_",
    values_to = "Prediction"
  ) |> 
  mutate(across(c(Truth, Prediction), ~ factor(
    .x, levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC")
  ))) |> 
  mutate(Method = fct_inorder(
    recode_values(
      Method,
      "hybrid_xgb_all" ~ "Hybrid-XGB, All Overlap",
      "hybrid_xgb_opt" ~ "Hybrid-XGB, Optimal",
      "hybrid_xgb_base" ~ "Hybrid-XGB, Base"
    )
  ))

# Validation set overall metrics
val_eval_overall <- val_pred_overall |>
  summarize(
    Accuracy = accuracy_vec(Truth, Prediction),
    Sensitivity = sensitivity_vec(Truth, Prediction),
    Specificity = specificity_vec(Truth, Prediction),
    `F1-Score` = f_meas_vec(Truth, Prediction),
    `Balanced Accuracy` = bal_accuracy_vec(Truth, Prediction),
    Kappa = kap_vec(Truth, Prediction),
    .by = Method
  ) |> 
  pivot_longer(cols = where(is.numeric),
               names_to = "Metric",
               values_to = "Overall")

# Validation set per-class metrics
val_eval_per_class <- val_pred_overall |>
  nest(.by = Method) |> 
  mutate(data = map(data, ~ ova_metrics(.x, Truth, Prediction, per_class_mset))) |> 
  unnest(data) |> 
  mutate(
    Metric = recode_values(
      .metric,
      "accuracy" ~ "Accuracy",
      "sensitivity" ~ "Sensitivity",
      "specificity" ~ "Specificity",
      "f_meas" ~ "F1-Score",
      "bal_accuracy" ~ "Balanced Accuracy",
      "kap" ~ "Kappa"
    ),
    .keep = "unused"
  ) |> 
  pivot_wider(
    id_cols = c(Method, Metric),
    names_from = class_group,
    values_from = .estimate
  )

# Combined all metrics
val_eval <-
  inner_join(val_eval_overall, val_eval_per_class, by = c("Method", "Metric"))

val_eval |> 
  kbl(booktabs = TRUE, linesep = "", digits = 3) |>
  kable_styling() |> 
  collapse_rows(columns = 1) |> 
  add_header_above(c(" " = 3, "Histotypes" = 5))
```

```{r}
#| label: fig-val-eval
#| fig-cap: 'Evaluation Metrics on Validation Set Models'
#| fig-height: 5.5

val_eval_long <- val_eval |>
  pivot_longer(cols = where(is.double),
               names_to = "Class",
               values_to = "Score") |>
  mutate(Method = fct_rev(Method),
         Metric = fct_inorder(Metric),
         Class = fct_inorder(Class))

ggplot(val_eval_long) +
  geom_tile(aes(x = Class, y = Method, fill = Score)) +
  geom_text(aes(x = Class, y = Method, label = round(Score, digits = 2)),
            size = 3) +
  facet_wrap(vars(Metric)) +
  scale_fill_viridis_c(option = "plasma",
                       breaks = c(0, 1),
                       limits = c(0, 1),
                       begin = 0.2) +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    axis.text.x.bottom = element_text(angle = 45, hjust = 1, vjust = 1),
    strip.text = element_text(face = "bold"),
    legend.position = "bottom",
    legend.direction = "horizontal"
  ) +
  labs(title = "Evaluation Metrics on Validation Set Models")
```

### Confusion Matrices

```{r}
#| label: fig-val-conf-mat
#| fig-cap: !expr get_plot_title()
#| fig-width: 10
#| out-width: '100%'

val_conf_mat <- val_pred_overall |>
  nest(.by = Method) |>
  deframe() |>
  imap(~ plot_conf_mat(data = .x, title = .y, cols = class_palette)) |>
  wrap_plots() +
  plot_annotation(title = "Confusion Matrix for Training Set Models evaluated on Validation Data", tag_levels = "A")

print(val_conf_mat)
```

### ROC Curves

::: {#val-roc-curves .panel-tabset .nav-pills}
#### All Overlap

```{r}
#| label: fig-val-roc-hybrid-xgb-all
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

val_roc_curve_hybrid_xgb_all <-
  plot_roc_curve(
    model = mod_hybrid_xgb,
    data = val_data,
    class = val_class,
    title = "ROC Curves for Hybrid-XGB, All Overlap Set Model in Validation Set",
    cols = class_palette
  )

print(val_roc_curve_hybrid_xgb_all)
```

#### Optimal Set

```{r}
#| label: fig-val-roc-hybrid-xgb-opt
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

val_roc_curve_hybrid_xgb_opt <- 
  plot_roc_curve(
    model = mod_hybrid_xgb_opt,
    data = val_data,
    class = val_class,
    title = "ROC Curves for Hybrid-XGB, Optimal Set Model in Validation Set",
    cols = class_palette
  )

print(val_roc_curve_hybrid_xgb_opt)
```

#### Base Set

```{r}
#| label: fig-val-roc-hybrid-xgb-base
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

val_roc_curve_hybrid_xgb_base <- 
  plot_roc_curve(
    model = mod_hybrid_xgb_base,
    data = val_data,
    class = val_class,
    title = "ROC Curves for Hybrid-XGB, Base Set Model in Validation Set",
    cols = class_palette
  )

print(val_roc_curve_hybrid_xgb_base)
```
:::

### Calibration Plots

::: {#val-calib .panel-tabset .nav-pills}
#### All Overlap

```{r}
#| label: fig-val-calib-hybrid-xgb-all
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_calib_curve(
  model = mod_hybrid_xgb,
  data = val_data,
  class = val_class,
  title = "Calibration Plots for Hybrid-XGB, All Overlap Set Model in Validation Set",
  cols = class_palette
)
```

#### Optimal Set

```{r}
#| label: fig-val-calib-hybrid-xgb-opt
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_calib_curve(
  model = mod_hybrid_xgb_opt,
  data = val_data,
  class = val_class,
  title = "Calibration Plots for Hybrid-XGB, Optimal Set Model in Validation Set",
  cols = class_palette
)
```

#### Base Set

```{r}
#| label: fig-val-calib-hybrid-xgb-base
#| fig-cap: !expr get_plot_title()
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

plot_calib_curve(
  model = mod_hybrid_xgb_base,
  data = val_data,
  class = val_class,
  title = "Calibration Plots for Hybrid-XGB, Base Set Model in Validation Set",
  cols = class_palette
)
```
:::

### Summary

A summary of the Hybrid-XGB, Optimal model results are shown in @fig-val-summary.

```{r}
#| label: fig-val-summary
#| fig-cap: 'Validation Summary'
#| fig-width: 11
#| fig-height: 6

val_conf_mat_simp <- val_conf_mat |> 
  pluck("meta", "patches", "plots", 2) +
  labs(title = "Confusion Matrix") +
  plot_annotation(title = NULL)

val_roc_curve_simp <- val_roc_curve_hybrid_xgb_opt +
  labs(title = "ROC Curves")

val_eval_grob <- 
  val_eval |> 
  filter(Method == "Hybrid-XGB, Optimal") |> 
  select(-Method) |> 
  flextable() |> 
  fontsize(size = 9, part = "all") |> 
  fontsize(size = 7, part = "header") |> 
  colformat_double(j = -1, digits = 3) |> 
  width(j = 1, width = 1.2) |>
  width(j = 3, width = 0.9) |>
  gen_grob(fit = "width", scaling = "fixed")

val_eval_gg <- ggplot() + 
  theme_void() + 
  annotation_custom(val_eval_grob)

layout <- "
AABBB
AABBB
CCBBB
CCBBB
"

val_conf_mat_simp + val_roc_curve_simp + val_eval_gg +
  plot_layout(design = layout) +
  plot_annotation(title = "Hybrid-XGB, Optimal Set Summary in Validation Set", tag_levels = "A") &
  theme(plot.tag = element_text(face = "bold"))
```

For a tree model, the "gain" is the most frequently used variable importance measure. It represents the fractional contribution of each feature to the model based on the total gain of this feature's splits. A higher percentage means higher importance. Figure @fig-final-model-vip shows the gain for the top 10 features of the final model (Hybrid-XGB).

```{r}
#| label: fig-final-model-vip
#| fig-cap: 'Final Model Variable Importance Plot'

# Final model
final_model <- mod_hybrid_xgb_opt |> extract_fit_engine() 

# Variable importance
final_vip <- vip(
  object = final_model,
  num_features = 10,
  include_type = TRUE,
  aesthetics = list(fill = "purple", width = 0.5)
) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  labs(title = "Feature Importance")

print(final_vip)
```

```{r}
#| label: tbl-gene-membership
#| tbl-cap: 'Detailed Gene Membership'

# Get all unique genes
cs1_genes <- cs1_norm$Name
cs2_genes <- cs2_norm$Name
cs3_genes <- cs3_norm$Name
unique_genes <- unique(c(cs1_genes, cs2_genes, cs3_genes))

# Determine gene membership
gene_membership <- tibble(
  Genes = unique_genes,
  CS1 = Genes %in% cs1_genes,
  CS2 = Genes %in% cs2_genes,
  CS3 = Genes %in% cs3_genes,
  PrOTYPE = Genes %in% overlap_PrOTYPE,
  SPOT = Genes %in% overlap_SPOT,
  Core = Genes %in% overlap_all,
  `All Overlap` = Genes %in% names(train_data),
  Complete = Genes %in% names(val_full_data),
  `Optimal-HXGB` = Genes %in% opt_genes_hybrid_xgb,
  `Optimal-SSVM` = Genes %in% opt_genes_smote_svm
) |>
  mutate(across(where(is.logical), ~ ifelse(.x, symbol$tick, "")))

# Interactive table to navigate various gene sets
datatable(
  gene_membership,
  options = list(
    scrollX = TRUE,
    fixedColumns = TRUE,
    columnDefs = list(
      list(
        targets = 1,
        render = JS("$.fn.dataTable.render.ellipsis( 10 )")
      ),
      list(type = "natural", targets = 0)
    ),
    pageLength = 50,
    dom = "Blfrtip",
    buttons = c("copy", "excel", "pdf"),
    lengthMenu = list(c(10, 50, 100, -1), c(10, 50, 100, "All"))
  ),
  rownames = FALSE,
  filter = "top",
  autoHideNavigation = TRUE,
  extensions = c("FixedColumns", "Buttons"),
  plugins = c("ellipsis", "natural")
)
```

### Additional Explorations

```{r}
#| label: tbl-val-pred-enoc-clin
#| tbl-cap: "Clinicopath characteristics between correct and incorrect predictions of ENOC cases"

od.otta <- od.otta |>
  mutate(otta_id = as.character(otta_id))

val_pred_enoc_clin <- val_pred_overall |>
  filter(Method == "Hybrid-XGB, Optimal") |> 
  inner_join(hist |> select(FileName, ottaID), by = "FileName") |>
  inner_join(od.otta, by = c("ottaID" = "otta_id")) |>
  inner_join(final_scores, by = "ottaID") |> 
  filter(Truth == "ENOC") |>
  mutate(
    Prediction_ENOC = factor(
      if_else(Prediction == "ENOC", "Predicted ENOC Correctly", "Missed ENOC")
    ) |>
      fct_rev(),
    stage_b1v234 = fct_collapse(
      stage_full,
      I = c("IA", "IB", "IC"),
      `II-IV` = c("IIA", "IIB", "IIC", "III(NOS)", "IIIA", "IIIB", "IIIC", "IV")
    ) |>
      droplevels(),
    race_white = fct_collapse(
      race,
      `non-white` = c("Asian", "other")
    ) |>
      droplevels(),
    arid1a_gr = fct_collapse(
      arid1a,
      `absent/subclonal` = c("absent", "subclonal")
    ) |>
      droplevels()
  )

val_pred_enoc_clin |>
  tbl_summary(
    by = Prediction_ENOC,
    label = list(
      age_dx ~ "Age at diagnosis",
      grade ~ "Tumour grade",
      stage_b1v234 ~ "FIGO tumour stage",
      race_white ~ "Race",
      arid1a_gr ~ "ARID1A",
      WT1 ~ "WT1",
      P53 ~ "TP53",
      PR ~ "PR",
      P16 ~ "P16",
      `NAPSIN A` ~ "NAPSIN A"
    ),
    include = c(age_dx, grade, stage_b1v234, race_white, arid1a_gr, WT1, P53, PR, P16, `NAPSIN A`)
  ) |>
  add_p() |>
  bold_labels() |>
  bold_p()
```

```{r}
#| label: fig-val-all-volcano
#| fig-cap: "Volcano Plots of Validation Set Predictions"
#| fig-width: 10
#| fig-height: 8

# Marina's thesis, Chapter 2
thesis_file <- here("data-raw/z5138799 PAVANELLO, Marina - Thesis chapter 2.pdf")

# Supplementary Table 2.1, All studies
table_2.1_all <-
  extract_tables(file = thesis_file, pages = 27:28) |>
  map(~ {
    dat <- select(., 1:5)
    headers <- find_header(dat = dat, "Genes" = 2)
    dat |>
      row_to_names(row_number = headers) |>
      rename(Rank = 1) |>
      filter(!Genes == "-") |>
      mutate(across(-Genes, as.numeric))
  }) |>
  bind_rows()

# Supplementary Table 2.1, Reduced studies
table_2.1_reduced <-
  extract_tables(file = thesis_file, pages = 27:29) |>
  map(~ {
    dat <- select(., 1, 6:9)
    headers <- find_header(dat = dat, "Genes" = 2)
    dat |>
      row_to_names(row_number = headers) |>
      rename(Rank = 1) |>
      mutate(across(-Genes, as.numeric))
  }) |>
  bind_rows()

# Supplementary Table 2.2, All studies
table_2.2_all <-
  extract_tables(file = thesis_file, pages = 30:37) |>
  map(~ {
    dat <- select(., 1:5)
    headers <- find_header(dat = dat, "Genes" = 2)
    dat |>
      row_to_names(row_number = headers) |>
      rename(Rank = 1) |>
      mutate(across(-Genes, as.numeric))
  }) |>
  bind_rows()

# Supplementary Table 2.2, Reduced studies
table_2.2_reduced <-
  extract_tables(file = thesis_file, pages = 30:31) |>
  map(~ {
    dat <- select(., 1, 6:9)
    headers <- find_header(dat = dat, "Genes" = 2)
    dat |>
      row_to_names(row_number = headers) |>
      rename(Rank = 1) |>
      mutate(across(-Genes, as.numeric))
  }) |>
  bind_rows()

# Gene ranks from all tables combined
all_gene_ranks <- bind_rows(
  `Total genes, All studies` = table_2.1_all,
  `Total genes, Reduced studies` = table_2.1_reduced,
  `Overlapping genes, All studies` = table_2.2_all,
  `Overlapping genes, Reduced studies` = table_2.2_reduced,
  .id = "List"
) |> 
  pivot_wider(
    id_cols = "Genes",
    names_from = "List",
    values_from = "Rank"
  )

# LGSOC differential gene expression analysis
val_lgsoc_condition <- val_pred_overall |>
  filter(Method == "Hybrid-XGB, Optimal", Truth == "LGSOC") |>
  mutate(Prediction_LSGOC = fct_other(
    Prediction,
    keep = "LGSOC",
    other_level = "non_LGSOC"
  ))

val_lgsoc_exp <- cs3 |>
  rename_all(~ gsub("^X", "", .)) |>
  select(Name, all_of(val_lgsoc_condition[["FileName"]])) |>
  column_to_rownames("Name")

dds_lgsoc <- DESeqDataSetFromMatrix(countData = val_lgsoc_exp,
                                   colData = val_lgsoc_condition,
                                   design = ~ Prediction_LSGOC)
dds_lgsoc <- dds_lgsoc[rowSums(counts(dds_lgsoc)) > 1, ]
dds_lgsoc <- DESeq(dds_lgsoc)

res_lgsoc <- dds_lgsoc |>
  results() |>
  as.data.frame() |>
  rownames_to_column(var = "Gene") |>
  left_join(all_gene_ranks, c("Gene" = "Genes")) |>
  semi_join(cs3 |> filter(Code.Class == "Endogenous"), by = c("Gene" = "Name")) |>
  as_tibble() |>
  mutate(
    Significant = case_when(
      padj < 0.05 & log2FoldChange > 2 ~ "Yes (Up)",
      padj < 0.05 & log2FoldChange < -2 ~ "Yes (Down)",
      .default = "No"
    ) |>
      factor(levels = c("No", "Yes (Up)", "Yes (Down)"))
  ) |>
  rowwise() |>
  mutate(`Marina's Sets` = any(!is.na(c_across(matches("genes"))))) |>
  ungroup()

# ENOC differential gene expression analysis
val_enoc_condition <- val_pred_overall |>
  filter(Method == "Hybrid-XGB, Optimal", Truth == "ENOC") |>
  mutate(Prediction_ENOC = fct_other(
    Prediction,
    keep = "ENOC",
    other_level = "non_ENOC"
  ))

val_enoc_exp <- cs3 |>
  rename_all(~ gsub("^X", "", .)) |>
  select(Name, all_of(val_enoc_condition[["FileName"]])) |>
  column_to_rownames("Name")

dds_enoc <- DESeqDataSetFromMatrix(countData = val_enoc_exp,
                                   colData = val_enoc_condition,
                                   design = ~ Prediction_ENOC)
dds_enoc <- dds_enoc[rowSums(counts(dds_enoc)) > 1, ]
dds_enoc <- DESeq(dds_enoc)

res_enoc <- dds_enoc |>
  results() |>
  as.data.frame() |>
  rownames_to_column(var = "Gene") |>
  left_join(all_gene_ranks, c("Gene" = "Genes")) |>
  semi_join(cs3 |> filter(Code.Class == "Endogenous"), by = c("Gene" = "Name")) |>
  as_tibble() |>
  mutate(
    Significant = case_when(
      padj < 0.05 & log2FoldChange > 2 ~ "Yes (Up)",
      padj < 0.05 & log2FoldChange < -2 ~ "Yes (Down)",
      .default = "No"
    ) |>
      factor(levels = c("No", "Yes (Up)", "Yes (Down)"))
  ) |>
  rowwise() |>
  mutate(`Marina's Sets` = any(!is.na(c_across(matches("genes"))))) |>
  ungroup()

# Combined volcano plot
res_all <-
  bind_rows(LGSOC = res_lgsoc, ENOC = res_enoc, .id = "Histotype") |>
  mutate(Histotype = fct_inorder(Histotype))

val_all_volcano <- ggplot(res_all, aes(x = log2FoldChange, y = -log10(padj))) +
  facet_wrap2(
    vars(Histotype),
    nrow = 1,
    scales = "free",
    strip = strip_themed(background_x = elem_list_rect(fill = class_palette[c(5, 3)]))
  ) +
  annotate("rect", xmin = 2, xmax = Inf, ymin = -log10(0.05), ymax = Inf,
           alpha = 0.2) +
  annotate("rect", xmin = -Inf, xmax = -2, ymin = -log10(0.05), ymax = Inf,
           alpha = 0.2) +
  geom_hline(yintercept = -log10(0.05), linetype = "dotted") +
  geom_vline(xintercept = c(-2, 2), linetype = "dotted") +
  geom_point(
    aes(shape = Significant, color = `Marina's Sets`),
    alpha = 0.5,
    stroke = 0.75,
    show.legend = TRUE
  ) +
  geom_text_repel(
    data = res_all |> filter(Significant != "No"),
    aes(label = Gene),
    size = 3,
    seed = 2025,
    max.overlaps = 25
  ) +
  scale_x_continuous(breaks = c(-6, -4, -2, 0, 2, 4)) +
  scale_color_manual(values = c("red", "forestgreen")) +
  scale_shape_manual(values = c(21, 2, 6), drop = FALSE) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    plot.caption = element_markdown(),
    axis.title = element_markdown(),
    strip.text = element_text(size = 12, face = "bold")
  ) +
  labs(
    x = "Log<sub>2</sub> Fold Change",
    y = "-Log<sub>10</sub> p-value",
    title = "Volcano Plots of Validation Set Predictions using Hybrid-XGB, Optimal",
    caption = "Significance condition: p<sub>adj</sub> < 0.05 and |log<sub>2</sub>FC| > 2"
  )

print(val_all_volcano)
```

```{r}
#| label: fig-bp-diff-exp-genes
#| fig-cap: 'Boxplot of Most Differentially Expressed Genes'
#| fig-height: 7
#| fig-width: 8
#| out-width: '100%'

bind_rows(
  Train = bind_cols(train_data, hist_final = train_class),
  Confirmation = bind_cols(conf_data, hist_final = conf_class),
  Validation = bind_cols(val_data, hist_final = val_class),
  .id = "Dataset"
) |>
  rownames_to_column("FileName") |> 
  select(Dataset, FileName, DKK4, hist_final) |>
  mutate(hist_final = factor(
    hist_final,
    levels = c("HGSOC", "CCOC", "ENOC", "MUOC", "LGSOC")
  )) |> 
  pivot_longer(
    cols = where(is.double),
    names_to = "Gene",
    names_ptypes = list(Gene = factor()),
    values_to = "Value"
  ) |>
  nest(.by = "Dataset") |>
  pmap(~ {
    ggboxplot(
      data = ..2,
      x = "hist_final",
      y = "Value",
      fill = "hist_final",
      palette = class_palette,
      facet.by = "Gene",
      xlab = "Histotype",
      ylab = "Normalized Expression",
      title = ..1,
      legend = "none"
    )
  }) |>
  wrap_plots(ncol = 1, axes = "collect") +
  plot_annotation(title = "Boxplot of Most Differentially Expressed Genes")
```

```{r}
#| label: fig-val-pred-protype
#| fig-cap: 'Subtype Prediction Summary among Predicted HGSOC Samples'
#| fig-height: 7
#| fig-width: 10
#| out-width: '100%'

val_pred_hgsoc_samples <- mod_hybrid_xgb |> 
  predict(val_data, type = "class") |> 
  bind_cols(val_data) |> 
  filter(.pred_class == "HGSOC") |> 
  rownames_to_column("FileName")

val_data_protype <- cs3_norm |>
  pivot_longer(
    cols = where(is.numeric),
    names_to = "FileName",
    names_prefix = "X",
    values_to = "Exp"
  ) |>
  pivot_wider(id_cols = FileName,
              names_from = "Name",
              values_from = "Exp") |>
  semi_join(val_pred_hgsoc_samples, by = "FileName") |>
  column_to_rownames("FileName")

val_pred_protype <- final_model |>
  predict(val_data_protype, type = "prob") |>
  as.data.frame() |>
  rownames_to_column("FileName") |>
  rowwise() |>
  mutate(prob = max(c_across(where(is.numeric))),
         entropy = entropy::entropy(c_across(matches("^C")), unit = "log2")) |>
  ungroup() |>
  bind_cols(Subtype = predict(final_model, val_data_protype, type = "class")) |> 
  add_count(Subtype) |> 
  mutate(median_entropy = median(entropy), .by = Subtype)

p1 <- ggplot(val_pred_protype, aes(x = Subtype, fill = Subtype)) +
  geom_text(aes(y = n, label = n),
            check_overlap = TRUE,
            nudge_y = 10) +
  geom_bar() +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  labs(y = "Count", title = "Distribution of Subtypes") +
  guides(fill = "none")

p2 <- ggplot(val_pred_protype, aes(x = Subtype, y = entropy, fill = Subtype)) +
  geom_boxplot() +
  geom_text(
    aes(
      y = median_entropy,
      label = number(median_entropy, prefix = "Median: ")
    ),
    check_overlap = TRUE,
    nudge_y = 0.1,
    size = 3
  ) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) +
  labs(x = "Subtype", y = "Entropy (log base 2)", title = "Distribution of Entropy") +
  guides(fill = "none")

p3 <- ggplot(val_pred_protype, aes(x = prob, y = entropy, color = Subtype)) +
  geom_point(alpha = 0.7) +
  theme_bw() +
  theme(
    panel.grid.minor = element_blank(),
    legend.position = "inside",
    legend.position.inside = c(0.96, 0.95),
    legend.justification.inside = c(1, 1),
    legend.box.background = element_rect(color = "black", linewidth = 1),
    legend.key.spacing.y = unit(-3, "pt")
  ) +
  labs(x = "Probability",
       y = "Entropy (log base 2)",
       title = "Probability by Entropy")

p <- wrap_plots(list(A = p1, B = p2, C = p3),
                design = "AB
                          CC") +
  plot_annotation(
    title = "Subtype Prediction Summary among Predicted HGSOC Samples",
    tag_levels = "A",
    theme = theme(plot.title = element_text(face = "bold"))
  )

print(p)
```
